---
title: "compliance_definition"
date: today
output:
  html_document
format:
  html:
    css: styles.css
    code-overflow: wrap
---
## From Michelle:

GOM - should be equal # of decl and logb

For SA, they need either a no fishing report weekly (due Tuesday following the fishing week, which is Mon-Sun) or they need a logbook for every fishing trip (so at least 1 per week if no fishing report is submitted).

Non-compliant vessels for the GOM, if 65 vessels are missing 1 report (1) is that a missing declaration or logbook?, (2) how many did they submit correctly (e.g. this month in question maybe they are missing 1 logbook, but they submitted 20. So, 1/20 = 5% missing). That is a vessel level, so then perhaps take the average of all for the month, and then the year, by region, and plot it that way.

```{r no cache setup, include=FALSE}
#| echo: false
library(grid)
source(r"(~\R_code_github\quantify_compliance\quantify_compliance_start.R)")
```

```{r setup, cache=TRUE, include=FALSE}

compl_clean_sa_vs_gom_plus_dual_short <-
  compl_clean_sa_vs_gom_plus_dual %>%
  select(
    vessel_official_number,
    year,
    week,
    gom_permitteddeclarations__,
    captainreports__,
    negativereports__,
    complianceerrors__,
    compliant_,
    week_start,
    permit,
    year_month,
    year_quarter
  )

# filter(permit == "sa_only")
# %>% names() %>% cat()
# select(-report2, -permit) # don't need' gom_permitteddeclarations__,
# )

## separate by permit
permit_dfs <- split(
  compl_clean_sa_vs_gom_plus_dual_short,
  compl_clean_sa_vs_gom_plus_dual_short$permit
)
setNames(permit_dfs, c("gom", "sa"))

str(permit_dfs)
```

## GOM examples
### GOM non-compliant & no errors == 0
```{r gom example 1}
# View(permit_dfs$gom)

permit_dfs$gom %>%
  filter(tolower(compliant_) == "no", complianceerrors__ == 0)
# 0
```

### GOM non-compliant & err > 0 == 2299
```{r gom example 2}
permit_dfs$gom %>% filter(tolower(compliant_) == "no", complianceerrors__ > 0)
# A tibble: 2,299 × 12
```

### GOM compliant & err > 0 == 7732
```{r gom example 3}
# (1)
permit_dfs$gom %>%
  filter(compliant_ == "YES", complianceerrors__ > 0)
# A tibble: 7,732 × 12
# TX6700JU   decl:5       logb:5       err:5       compl:YES      week_of:2022-12-26
```

### GOM non-compliant  & # declarations != # logbooks
```{r gom example 4}
# (4)
permit_dfs$gom %>%
  filter(tolower(compliant_) == "no",
         !(gom_permitteddeclarations__ == captainreports__))
# A tibble: 995 × 12
# FL4915LT   decl:4       logb:3       err:3       compl:NO      week_of:2022-12-26
```

### GOM non-compliant & # declarations == # logbooks
```{r gom example 5}
# (3)
permit_dfs$gom %>%
  filter(tolower(compliant_) == "no",
         gom_permitteddeclarations__ == captainreports__)

# FL7991RP   decl:1       logb:1       err:2       compl:NO      week_of:2022-12-26

# (2)
# FL9520RN   decl:5       logb:3       err:3       compl:YES      week_of:2022-12-26

```

## SA examples
### SA non_compliant & DNF + logbooks > 0
```{r SA example 1}
# SA ----
permit_dfs$sa %>%
  filter(tolower(compliant_) == "no",
         negativereports__ + captainreports__ > 0)

```

```{r aux function}
#| echo: false

my_names <- c(
  "vessel_official_number",
  "year",
  "week",
  "gom_permitteddeclarations__",
  "logb",
  "negativereports",
  "err",
  "compl",
  "week_of",
  "permit",
  "year_month",
  "year_quarter"
)

print_line <- function(df_row) {
  # df_row = sa_1[1, ]
  
  my_names %>%
    paste(df_row, sep = ': ') %>%
    str_remove('_NA') %>% cat(sep = ", ")
}
```

### SA compliant & no reports: 1408
```{r SA example 2}
sa_1 <-
  permit_dfs$sa %>%
  filter(tolower(compliant_) == "yes",
         (captainreports__ + negativereports__) == 0)
# complianceerrors__
# A tibble: 1,408 × 12
sa_1

# print_line(sa_1[1, ])
# MC7540US, logb: 0, negativereports: 0, err: 0, compl: YES, week_of: 12/26/2022
```

### SA compliant & have reports & err > 0
```{r SA example 3}
sa_2 <-
  permit_dfs$sa %>%
  filter(
    tolower(compliant_) == "yes",
    (captainreports__ + negativereports__) > 0,
    complianceerrors__ > 0
  )
sa_2

# print_line(sa_2[1, ])
# FL1125AX, logb: 1, negativereports: 0, err: 1, compl: YES, week_of: 2022-09-19
```

### SA non_compliant & # reports > 0
```{r SA example 4}

sa_3 <-
  permit_dfs$sa %>%
  filter(tolower(compliant_) == "no",
         (captainreports__ + negativereports__) > 0,
  )

# complianceerrors__ == 0
sa_3

# print_line(sa_3[4, ])
# FL8074DA, logb: 0, negativereports: 7, err: 1, compl: NO, week_of: 2022-12-26

```

### SA non_compliant & has logbooks
```{r SA example 5}

sa_4 <-
  permit_dfs$sa %>%
  filter(tolower(compliant_) == "no",
         (captainreports__) > 0
         )
# complianceerrors__ == 0
sa_4
# 2 940476      2022  45: …       0       2       0 1       NO      2022-11-07 sa_on… Nov 20…
# print_line(sa_4[2, ])
# 940476, logb: 2, negativereports: 0, err: 1, compl: NO, week_of: 2022-11-07

```

## Questions from Michelle
```{r GOM what\'s missing }
# non-compliant vessels for the GOM, if 65 vessels are missing 1 report (1) is that a missing declaration or logbook?,

### --- get non compliant vessel_ids ----
non_compl_vessel_id_gom <-
  permit_dfs$gom %>%
  filter(tolower(compliant_) == "no") %>%
  select(vessel_official_number) %>%
  unique()

str(non_compl_vessel_id_gom)
# tibble [1,849 × 1] (S3: tbl_df/tbl/data.frame)

non_compl_gom <-
  inner_join(permit_dfs$gom, non_compl_vessel_id_gom)
# Joining with `by = join_by(vessel_official_number)`
str(non_compl_gom)
# tibble [81,612 × 12] (S3: tbl_df/tbl/data.frame)

```

### Check by week
```{r Check by week}

## --- check by week ----
gom_id_reports_one_week <-
  non_compl_gom %>%
  filter(week_start == "2022-12-26") %>%
  # dplyr::glimpse()
  # Rows: 47
  select(gom_permitteddeclarations__,
         captainreports__,
         vessel_official_number,
         compliant_)

glimpse(gom_id_reports_one_week)

gom_id_reports_one_week_longer <-
  gom_id_reports_one_week %>%
  rename(decl = gom_permitteddeclarations__,
         logb = captainreports__) %>%
  tidyr::pivot_longer(cols = c(decl,
                        logb),
               names_to = "report_type",
               values_to = "report_count") %>% 
  dplyr::mutate(id_compl = paste(vessel_official_number, compliant_, sep = "_"))
# %>%
#   select(-c(vessel_official_number, compliant_))
# %>%
#   dplyr::glimpse()

gom_plot_1week <- 
  ggplot(gom_id_reports_one_week_longer,
       aes(x = vessel_official_number, y = report_count, fill = report_type
           )
       ) + 
  geom_bar(stat = "identity")

adds <-
  theme(axis.text.x = element_blank(),
        # axis.text.y = element_text(angle = 45)
        )

my_labs <- 
labs(title = "1 Week",
     x ="Vessel official number", y = "report count official number")
  
gom_plot_1week + adds + my_labs

# === logb - decl ===

gom_id_reports_one_week_l_d <-
  gom_id_reports_one_week %>%
  rename(decl = gom_permitteddeclarations__,
         logb = captainreports__) %>%
  dplyr::mutate(logb_decl = as.numeric(logb) - as.numeric(decl))


# compl_clean_sa_vs_gom_plus_dual_short %>%
#   filter(vessel_official_number == "VA7344AW",
#          week_start == "2022-12-26"
#   )

gom_id_reports_one_week_l_d %>% head()

gom_plot_1week_ld <- 
  ggplot(gom_id_reports_one_week_l_d,
         aes(x = vessel_official_number, y = logb_decl, fill = compliant_
         )
  ) + 
  geom_bar(stat = "identity")

gom_plot_1week_ld +
  labs(title = "1 Week",
       x ="Vessel official number", y = "# logbook - # decl") + adds
```

