---
title: "Looking at the proportion of compliant and non-compliant vessels per different time periods and permit groups"
date: 2023-03-22
output: 
  html_document
format:
  html:
    css: styles.css
    code-overflow: wrap
---

## Set up

```{r no cache setup, include=FALSE}
# additional libraries
library(zoo)
library(gridExtra)
library(cowplot)

source("~/R_code_github/useful_functions_module.r")
```

```{r setup, cache=TRUE, include=FALSE}
# knitr::opts_chunk$set(tidy=TRUE)
my_paths <- set_work_dir()
root.dir <- my_paths
source("~/R_code_github/quantify_compliance/get_data.R")

```

```{r, cache=TRUE}
glimpse(compl_clean)
# Rows: 167,607
# Columns: 21

```

## Separate SA and GOM permits

#### get list of all permitgroups

https://www.fisheries.noaa.gov/southeast/recreational-fishing/frequently-asked-questions-southeast-hire-integrated-electronic#general-program-requirements

GOM: RCG, HRCG, CHG, HCHG

SA: CDW, CHS, SC

### add a column for our permit groups

```{r separate into 2 groups: SA vs GOM + dual}
compl_clean_sa_vs_gom_plus_dual_0 <-
  compl_clean %>%
  dplyr::mutate(permit =
           dplyr::case_when(
             !grepl("RCG|HRCG|CHG|HCHG", permitgroup) ~ "sa_only",
             .default = "gom"
           ))

glimpse(compl_clean_sa_vs_gom_plus_dual_0)
```

## add a column for months

```{r add a column for months}
compl_clean_sa_vs_gom_plus_dual <-
  compl_clean_sa_vs_gom_plus_dual_0 %>%
  # add month
  dplyr::mutate(year_month = as.yearmon(week_start))

glimpse(compl_clean_sa_vs_gom_plus_dual)
```

### view fewer columns for a test

```{r view fewer columns}

compl_clean_sa_vs_gom_plus_dual %>%
  select(vessel_official_number, compliant_, week, permit, year_month, year) %>%
  # dplyr::arrange(year, week, permit, vessel_official_number) %>%
  head()

```

## Percentage

From Michelle:

Can we make the titles, "weekly compliance Gulf and dual permitted", "monthly compliance Gulf and dual permitted", "annual compliance Gulf and dual permitted", and then the same for SA. So 6 total figures.

Oh, and show it not as a number but a proportion. So, if we were looking at Gulf weekly compliance and it was 50 compliant vessels and 50 non-compliant, then the figures would be showing bars for 50% compliant and 50% non compliant. (50/100\*100= 50%)

We don't want to sum the entries though. We just need to know vessel level compliance, weekly, monthly and annually. How many vessels by gulf and SA. The file you have lists the compliance by vessel and permit type, so you'll just need to analyze it that way.

### Prepare compliance info

#### Get only the columns we need

```{r Prepare compliance info}
compl_clean_sa_vs_gom_plus_dual_short <-
  compl_clean_sa_vs_gom_plus_dual %>%
  select(
    vessel_official_number,
    compliant_,
    permit,
    week_start,
    year_month,
    year
  )

head(compl_clean_sa_vs_gom_plus_dual_short)
```

#### Create 2 new dfs for SA and GOM + dual permit groups

```{r}
sa_compl_clean_sa_vs_gom_plus_dual_short <-
  filter(compl_clean_sa_vs_gom_plus_dual_short, permit == "sa_only")
gom_compl_clean_sa_vs_gom_plus_dual_short <-
  filter(compl_clean_sa_vs_gom_plus_dual_short, permit == "gom")
```

#### an auxilary percent function

```{r my_percent fun}
my_percent <- function(x, y) {
  # y : 100%
  # x : b%
  return(x * 100 / y)
}

```

#### an auxilary function to get time period field name from df names

```{r time period field name fun}

get_time_period_col_name <- function(my_df) {
  my_df %>%
    select(-count, -starts_with("percent")) %>%
    names() %>%
    return()
}
  
```

#### function percent_by_time_period

```{r percent_by_time_period fun}
percent_by_time_period <- function(my_df, time_period_field_name) {
  my_df %>%
    dplyr::group_by(!!sym(time_period_field_name)) %>%
    # add columns
    summarize(
      # count by group
      count = n(),
      # percent of yeses to all
      percent_yes = my_percent(sum(compliant_ == "YES"), count),
      # percent of nos to all
      percent_no = my_percent(sum(compliant_ == "NO"), count) # the same as "100 - percent_yes"
    ) %>%
    return()
}
```

#### create individual dfs by permit region and time period

```{r individual dfs by permit region and time period}

gom_per_year <-
  percent_by_time_period(gom_compl_clean_sa_vs_gom_plus_dual_short, "year")

gom_per_month <-
  percent_by_time_period(gom_compl_clean_sa_vs_gom_plus_dual_short, "year_month")

gom_per_week <-
  percent_by_time_period(gom_compl_clean_sa_vs_gom_plus_dual_short, "week_start")

sa_per_year <-
  percent_by_time_period(sa_compl_clean_sa_vs_gom_plus_dual_short, "year")

sa_per_month <-
  percent_by_time_period(sa_compl_clean_sa_vs_gom_plus_dual_short, "year_month")

sa_per_week <-
  percent_by_time_period(sa_compl_clean_sa_vs_gom_plus_dual_short, "week_start")
```

#### test one random week

##### data:

```{r}
#| classes: test

sa_compl_clean_sa_vs_gom_plus_dual_short %>%
  filter(week_start == "2022-12-26") %>%
  dplyr::glimpse()
```

##### % from the function result:
GOM + dual
```{r function result GOM}
#| classes: test
gom_per_week %>%
 filter(week_start == "2022-12-26")
```

SA
```{r function result}
#| classes: test
sa_per_week %>%
 filter(week_start == "2022-12-26")
```

percent_yes = **58.2**

##### step by step:

```{r step by step}
#| classes: test
sa_compl_clean_sa_vs_gom_plus_dual_short %>%
  filter(week_start == "2022-12-26") %>%
  dplyr::group_by(compliant_, week_start) %>%
  summarise(count = n())
```

no + yes = 684 + 953 = 1637 (100%)

"yes" \* 100 / 1637 = `r my_percent(953, (684 + 953))`%

percent "YES" vessels (= compliant vessels):

```{r}
my_percent(953, (684 + 953))
```

Percent of a "YES" for this week is **58.2**

##### inside the function:

```{r show inside the function}
#| classes: test
sa_compl_clean_sa_vs_gom_plus_dual_short %>%
  filter(week_start == "2022-12-26") %>%
  dplyr::group_by(week_start) %>%
  summarise(count = n(),
      percent_yes = my_percent(sum(compliant_ == "YES"), count),
      percent_no = my_percent(sum(compliant_ == "NO"), count) # the same as "100 - percent_yes"
    )
```

percent_yes = **58.2**

### plots for percentage

```{r define variables}

my_regions <- c("Gulf and dual", "South Atlantic")

my_colors <- c("red", "blue")

names(sa_per_year)
```

```{r plots for percentage}
percent_plot <- function(my_df,
                         region #SA vs. GOM + dual, see my_regions
                         ) {
  # get the current time period field name
  time_period <- get_time_period_col_name(my_df)
  
  # make a plot
  percent_p <-
    my_df %>%
    tidyr::pivot_longer(
      # which columns to pivot
      starts_with("percent"),
      # pivot column names go to a new "key" column
      names_to = "key",
      # pivot values go to a new "percent" column
      values_to = "percent") %>%
    ggplot(aes(
      # "year" etc. column names for x
      x = !!sym(time_period),
      y = percent,
      fill = key
    ))
  
  # rename column names for titles
  my_title <- dplyr::case_when(
    time_period == "year" ~ "Annual",
    time_period == "year_month" ~ "Monthly",
    time_period == "week_start" ~ "Weekly"
  )
  
  # rename column names for x labels
  my_x_lab <- dplyr::case_when(
    time_period == "year" ~ "year",
    time_period == "year_month" ~ "month",
    time_period == "week_start" ~ "week"
  )
  
  # improve the plot view
  percent_p + 
    # side by side bars
    geom_bar(position = "dodge", stat = "identity") +
    # labels
    labs(
      title = paste0(my_title, " compliance"),
      y = "",
      x = my_x_lab
    ) +
    # Change colors manually
    scale_fill_manual(
      # what colors to use
      values = my_colors,
      # The legend title and labels
      name = "Colors",
      labels = c("% non-compliant", "% compliant")) +
    # rotate x labels
    theme(axis.text.x = element_text(angle = 45)) +
    # make Y axis go to 100
    ylim(0, 100) %>%
    return()
}
```

#### create individual plots

```{r create individual plots}
sa_per_year_p <- percent_plot(sa_per_year, my_regions[[2]])
sa_per_month_p <- percent_plot(sa_per_month, my_regions[[2]])
sa_per_week_p <- percent_plot(sa_per_week, my_regions[[2]])

gom_per_year_p <- percent_plot(gom_per_year, my_regions[[1]])
gom_per_month_p <- percent_plot(gom_per_month, my_regions[[1]])
gom_per_week_p <- percent_plot(gom_per_week, my_regions[[1]])
```

#### save the legend separately

```{r legend}
legend <-
  cowplot::get_legend(gom_per_week_p)
```

#### combine SA plots

```{r combine plots SA}

# SA
region <- my_regions[[2]]
grid.arrange(
  sa_per_week_p + theme(legend.position = 'hidden'),
  sa_per_month_p + theme(legend.position = 'hidden'),
  sa_per_year_p + theme(legend.position = 'hidden') +
    # add % on top of the bars
    geom_text(aes(label =
                    paste0(round(percent, 2), "%")
                  ),
              position = position_dodge(width = 0.9),
              vjust = -0.25),
  legend,
  nrow = 2,
  top = paste0(region, " permitted"),
  left = "YES and NO percentage"
)
```

#### combine GOM + dual plots

```{r combine plots GOM + dual}

# GOM + dual
region <- my_regions[[1]]
grid.arrange(
  gom_per_week_p + theme(legend.position = 'hidden'),
  gom_per_month_p + theme(legend.position = 'hidden'),
  gom_per_year_p + theme(legend.position = 'hidden') + 
    # add % on top of the bars
    geom_text(aes(label = 
                    paste0(round(percent, 2), "%")
                  ),
              position = position_dodge(width = 0.9),
              vjust = -0.25),
  legend,
  nrow = 2,
  top = paste0(region, " permitted"),
  left = "YES and NO percentage"
)

```
