---
title: Non compliant SA only permitted vessels (2022) by home port
---
Identifying any particular areas of high non-compliance to help focus future outreach efforts. 

```{r no cache setup, results='hide', message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}

# A general-purpose tool for dynamic report generation in R
library(knitr)

# Adds features to a kable output
library(kableExtra)

# Format R code automatically
library(styler)

```

```{r df format setup}
#| include: false
# kable <- function(data) {
#   knitr::kable(data, booktabs = true, digits = 2) %>%
#     kable_styling('striped', full_width = FALSE)
# }

knit_print.data.frame = function(x, ...) {
  res = paste(c(
    '',
    '',
    knitr::kable(x, digits = 2) |>
      kableExtra::kable_styling('striped', full_width = FALSE)
  ),
  collapse = '
')
  knitr::asis_output(res)
}

registerS3method(
  'knit_print', 'data.frame', knit_print.data.frame,
  envir = asNamespace('knitr')
)

# knitr::opts_chunk$set(echo = TRUE)

# options(knitr.table.format = 'HTML')


```

# setup current project
```{r setup current project, results='hide', message=FALSE, warning=FALSE}
# identifying any particular areas of high non-compliance to help focus future outreach efforts. 
# do this as a map

# home port from the permit as an area

# source the usual setup 
# get data
# remove not in metrics
# separate by permit region
# remove not in Jeannette's SA list
# remove not in Jeannette's GOM list
# add home port

# Load the 'mapview' library for interactive viewing of spatial data.
library(mapview)
library(leafpop)

if (!require(tidygeocoder)) {
  install.packages("tidygeocoder")
  library(tidygeocoder)
}
# help(tidygeocoder)

## Load the 'tigris' package to access geographic data.
library(tigris)
## Set the 'tigris_use_cache' option to TRUE. This will enable caching of
## data retrieved from the TIGER/Line Shapefiles service, which can help
## improve data retrieval performance for future sessions.
tigris_use_cache = TRUE

source("~/R_code_github/useful_functions_module.r")
my_paths <- set_work_dir()

current_project_dir_path <- this.path::this.dir()

current_project_dir_name <- basename(current_project_dir_path)
```

## prepare data 

```{r prepare data}
# prepare data ----
get_data_file_path <-
  file.path(my_paths$git_r,
            current_project_dir_name,
            "non_compliant_areas_get_data.R")

source(get_data_file_path)
# all_get_db_data_result_l
# vessels_permits_home_port_lat_longs_city_state

# vessels_permits_home_port_lat_longs_city_state |> dim()
# [1] 4729    6
```

### check for duplicate vessels 

```{r check for duplicate vessels}
## check for duplicate vessels ----
vessels_permits_home_port_lat_longs_city_state |>
  distinct() |>
  group_by(SERO_OFFICIAL_NUMBER) %>%
  filter(n() > 1) |>
  dim()
# 0
```

### check how many coords have more than one vessel 

```{r check how many coords have more than one vessel}
## check how many coords have more than one vessel ----
vessels_permits_home_port_lat_longs_city_state |>
  distinct() |>
#   group_by(permit_sa_gom, lat, long) %>%
# [1] 4393    6
  group_by(lat, long) %>%
  filter(n() > 1) |>
  dim()
# [1] num of SERO_OFFICIAL_NUMBER    6
```

## add counts to vessel_permit 
Adding a count column with num of SERO_OFFICIAL_NUMBER based on permit type, latitude, and longitude to the data frame.

```{r add counts to vessel_permit}
# add counts to vessel_permit ----
# Adding a count column with num of SERO_OFFICIAL_NUMBER based on permit type, latitude, and longitude to the data frame.

vessels_permits_home_port_lat_longs_city_state_cnt_vsl_by_port <-
  vessels_permits_home_port_lat_longs_city_state |>
  dplyr::add_count(permit_sa_gom,
                   lat,
                   long,
                   name = "cnt_vsl_by_permit_n_port_coord")
```

#### check counts 

```{r check counts}
### check counts ----
vessels_permits_home_port_lat_longs_city_state_cnt_vsl_by_port |>
  select(SERO_OFFICIAL_NUMBER,
         permit_sa_gom,
         lat,
         long) |>
  count(permit_sa_gom,
        lat,
        long) |>
  filter(permit_sa_gom == "sa_only") |>
  arrange(desc(n)) |>
  head()

vessels_permits_home_port_lat_longs_city_state_cnt_vsl_by_port |>
  filter(permit_sa_gom == "sa_only") |>
  select(-SERO_OFFICIAL_NUMBER) |> 
  distinct() |> 
  arrange(desc(cnt_vsl_by_permit_n_port_coord)) |>
  head()
```

## Join home port and compliance info by vessel 
This code filters and modifies the data based on the permit type and compliance status for the year 2022. Here's the breakdown of the comments:

1. Filtering and modifying data based on permit type and compliance status.

2. Using the pipe operator (`|>`) to pass the data frame `vessels_permits_home_port_lat_longs_city_state_cnt_vsl_by_port` to the subsequent functions.

3. Filtering rows where the permit type is "sa_only" using the `filter` function.

4. Adding a new column named 'is_compliant_in_22' using the `mutate` function and conditional logic (`case_when`):
   - If the vessel's official number is in a specific list (`compl_err_db_data_metrics_permit_reg_sa_only_vsl$vessel_official_nbr`), set compliance status to "NO".
   - For other vessels, default compliance status to "YES".

```{r Join home port and compliance info by vessel}
# Join home port and compliance info by vessel ----


vessels_permits_home_port_lat_longs_city_state_sa_compliance <-
  vessels_permits_home_port_lat_longs_city_state_cnt_vsl_by_port |>
  dplyr::filter(permit_sa_gom == "sa_only") |>
  dplyr::mutate(
    is_compliant_in_22 = 
      dplyr::case_when(
      SERO_OFFICIAL_NUMBER %in% compl_err_db_data_metrics_permit_reg_sa_only_vsl$vessel_official_nbr ~ "NO",
      .default = "YES"
    )
  )

dim(vessels_permits_home_port_lat_longs_city_state_sa_compliance)
# [1] 25587    33
# [1] 4741    7 distinct
# [1] 4729    7 no comp only
# [1] 3388    8 sa only


# data_overview(vessels_permits_home_port_lat_longs_city_state_sa_compliance)
# all permit regions
# SERO_OFFICIAL_NUMBER 4729
# lat                   547
# is_compliant_in_22                2

# sa_only
# SERO_OFFICIAL_NUMBER           3388
# lat                             450
# is_compliant_in_22                2
```

## count vessels by home_port and compliance 
Adding a count column named cnt_sa_vsl_by_port_coord_n_compl based on the variables lat, long, and is_compliant_in_22 using the dplyr::add_count function.

```{r count vessels by home_port and compliance}
# count vessels by home_port and compliance ----

vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt <-
  vessels_permits_home_port_lat_longs_city_state_sa_compliance |>
  dplyr::add_count(lat,
                   long,
                   is_compliant_in_22,
                   name = "cnt_sa_vsl_by_port_coord_n_compl")
```

### check if total vessel num is always grater than non compliant vessels 

```{r check if total vessel num is always grater than non compliant vessels}
## check if total vessel num is always grater than non compliant vessels ----
vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt |> 
  dplyr::filter(cnt_vsl_by_permit_n_port_coord < cnt_sa_vsl_by_port_coord_n_compl) |> 
  dim()
0
# correct
```

## Percent of (non)compliant by port 
Adding new columns to the data frame:

non_comp_perc: Non-compliance percentage calculated as the ratio of non-compliant vessels to total vessels.
is_comp_perc_round: Rounded percentage of non-compliance. No digits after the decimal point.

```{r Percent of (non)compliant by port}
# Percent of (non)compliant by port ----

vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc <-
  vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt |>
  dplyr::group_by(is_compliant_in_22) |>
  dplyr::mutate(
    non_comp_perc =
      cnt_sa_vsl_by_port_coord_n_compl * 100 /
      cnt_vsl_by_permit_n_port_coord,
    is_comp_perc_round =
      round(non_comp_perc)
  ) |>
  dplyr::ungroup()

glimpse(vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc)
# [1] 3388   11
```

## spot test counts 

```{r spot test counts}
# spot test counts ----
vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc |> 
  filter(city_fixed == "SEBASTIAN") |> 
  data_overview()
# SERO_OFFICIAL_NUMBER 27
# is_comp               2

vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc |> 
  filter(city_fixed == "SEBASTIAN") |> 
  select(-SERO_OFFICIAL_NUMBER) |> 
  distinct() |> 
  glimpse() |>
  knitr::kable(caption = "")
# $ is_compliant_in_22               <chr> "NO", "YES"
# $ cnt_sa_vsl_by_port_coord_n_compl <int> 15, 12
# $ is_comp_perc_round               <dbl> 55.6, 44.4
```

### check multiple names for the same cooordinates 

```{r check multiple names for the same cooordinates}
## check multiple names for the same cooordinates ---- 
# mult_names <- "AMELIA"
# BAYOU LA BATRE
mult_names <- "BATRE"
vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc |>
  filter(grepl(mult_names, city_fixed)) |>
  select(-SERO_OFFICIAL_NUMBER) |> 
  distinct() |>
  glimpse() |>
  knitr::kable(caption = "")
# $ SERO_OFFICIAL_NUMBER             <chr> "938369", "FL3307AE"
# $ city_fixed                       <chr> "AMELIA IS", "AMELIA ISLAND"
# $ cnt_vsl_by_permit_n_port_coord   <int> 2, 2


# $ city_fixed                       <chr> "BAYOU LA BATRE", "BAYOU  LA BATRE"…
# $ state_fixed                      <chr> "AL", "AL", "LA"
# $ cnt_vsl_by_permit_n_port_coord   <int> 103, 103, 103
```

## convert to sf 

```{r convert to sf}
# convert to sf ----
```

### how many don't have coords 

```{r how many don_t have coords}
## how many don't have coords ----
vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc |>
  filter(is.na(long) &
           is.na(lat)) |>
  dim()
# 11
```

### Preparing spatial data for map visualization 

Filtering rows with non-missing longitude and latitude values using the filter function.

Converting the data frame to a spatial object using the sf::st_as_sf function.

Specifying the field names ("long", "lat") to be used as coordinates.

Setting the Coordinate Reference System (CRS) for the spatial object to match the US states map using the crs parameter with the tigris_crs value.

```{r Preparing spatial data for map visualization}
## Preparing spatial data for map visualization ----

vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf <-
  vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc |>
  dplyr::filter(!is.na(long) &
           !is.na(lat)) |>
  sf::st_as_sf(coords = c("long", "lat"),
               crs = tigris_crs)

all_home_ports <-
  mapview(vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf)
```

### crop all home ports by us state south map 
Creating a subset of data for the southern and eastern coast states

```{r crop all home ports by us state south map}
## crop all home ports by us state south map ----
vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south <-
  vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf |>
  sf::st_crop(south_east_coast_states_shp_bb)  # Bounding box used for cropping
# although coordinates are longitude/latitude, st_intersection assumes that they
# are planar
# Warning message:
# attribute variables are assumed to be spatially constant throughout all geometries 

dim(vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south)
# [1] 3106   10
```

## Prepare for mapping: non compl only, add labels 
The following code modifies the data frame for map visualization by filtering, selecting distinct rows, and creating new columns. Here's the breakdown of the comments:

1. Modifying the data frame for map visualization.

2. Using the pipe operator (`|>`) to pass the data frame `vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south` to the subsequent functions.

3. Filtering rows where the compliance status in 2022 is "NO" using the `filter` function.

4. Keeping only distinct rows in the data frame using the `distinct` function.

5. Adding a new column named 'my_label' using string interpolation with the `str_glue` function. This column combines the city, state, and non-compliance percentage for labeling on the map.

6. Adding a new column named 'perc_nc_bin' using the `cut_number` function. This column represents the non-compliance percentage binned into 5 levels for color representation on the map.

```{r Prepare for mapping: non compl only, add labels}
# Prepare for mapping: non compl only, add labels ----


vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south_lab <-
  vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south |>
  dplyr::filter(is_compliant_in_22 == "NO") |>
  dplyr::distinct() |> 
  dplyr::mutate(my_label =
           stringr::str_glue("{city_fixed} {state_fixed}; {is_comp_perc_round}% non-compl")) |> 
  dplyr::mutate(perc_nc_bin = 
                  ggplot2::cut_number(is_comp_perc_round, n = 5))

# View(vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south_lab)

dim(vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south_lab)
# [1] 832  12
```

### Calculating the number of unique colors based on a specific column

```{r Calculating the number of unique colors based on a specific column}
# Calculating the number of unique colors based on a specific column ----
uniq_color_num <-
  function(zcol_name) {
    length(
      unique(
        vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south_lab[[zcol_name]]
      )
    ) %>%
      return()
  }
# uniq_color_num("is_comp_perc_round")
# 43
```

### pop-up marker table
The following code creates pop-up marker information for the map by renaming columns and generating a pop-up table. Here's the breakdown of the comments:

1. Creating pop-up marker information for the map using the `leafpop::popupTable` function.

2. Using the pipe operator (`|>`) to pass the data frame `vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south_lab` to the subsequent functions.

3. Renaming columns in the data frame for clarity in pop-up information. The column `cnt_vsl_by_permit_n_port_coord` is renamed to `total_vsls`, and `cnt_sa_vsl_by_port_coord_n_compl` is renamed to `non_compliant`.

4. Generating a pop-up table using the specified columns (`total_vsls`, `non_compliant`, and `perc_nc_bin`) with the `leafpop::popupTable` function.

5. Disabling the display of feature ID in the pop-up table by setting `feature.id` to FALSE.

6. Disabling the display of row numbers in the pop-up table by setting `row.numbers` to FALSE.

7. Specifying the columns to be displayed in the pop-up table using the `zcol` parameter.

```{r pop-up marker table}
## pop-up marker table ----
markers_info <-
  vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south_lab |>
  dplyr::rename(total_vsls = cnt_vsl_by_permit_n_port_coord,
         non_compliant = cnt_sa_vsl_by_port_coord_n_compl,) |>
  leafpop::popupTable(
    feature.id = FALSE,
    row.numbers = FALSE,
    zcol = c(
      "total_vsls",
      "non_compliant",
      "perc_nc_bin"
    )
  )
```

### mapview
```{r mapview}
## mapview ----
vessels_permits_home_port_lat_longs_city_state_sa_compliance_cnt_perc_sf_south_lab |>
  mapview::mapview(
    label = "my_label",
    # Specifying the column to be used for coloring the map
    zcol = "perc_nc_bin",
    # Scaling factor for the size of the markers
    cex = "cnt_vsl_by_permit_n_port_coord",
    # Setting the transparency level of the markers
    alpha = 0.3,
    # Specifying the color palette for the map
    # The direction parameter is set to -1 to reverse the order of colors.
    col.regions =
      viridisLite::mako(uniq_color_num("perc_nc_bin"), direction = -1),
    # legend = FALSE,
    layer.name = '% non compliant SA permitted vessels (2022) by home port coordinates',
    popup = markers_info
    # Enabling burst mode for each bin to be a layer
    # burst = TRUE 
  # )
) +
  south_east_coast_states_shp
```

