---
title: "Compare catch in MRIP survey vs. FHIER logbooks"
subtitle:  "(see read.me)"
date: today
project:
  lib-dir: ..
format:
  html:
    toc: true
    # toc-depth: 2
    css: styles.css
    code-overflow: wrap
    code-fold: true
    code-summary: "Show the code"
    code-line-numbers: true
---

```{r no cache setup, include=FALSE}
##| echo: false
library(zoo)
library(gridExtra)

# include auxilary functions
source("~/R_code_github/useful_functions_module.r")
my_paths <- set_work_dir()
```

```{r setup, cache=TRUE, include=FALSE}
##| echo: false

source("~/R_code_github/compare_catch/get_data.R")

```

## FHIER data

### Get field names into variables

```{r logbooks_content }
# There are different formats in different available files.
# Find a column name with "itis" in it
itis_field_name <- grep("itis", names(logbooks_content), value = T)
# catch_species_itis

# Same for "vessel.*official"
vessel_id_field_name <-
  grep("vessel.*official", names(logbooks_content), value = T)
# vessel_official_nbr

```

### Clean logbooks_content

```{r clean logbooks_content }

fhier_logbooks_content <-
  logbooks_content  %>%
  # create a new column
  mutate(trip_start_date_time =
    # trip start: combine a date without time, a space and a time
    paste(substr(trip_start_date, 1, 10),
    trip_start_time)) %>%
  # Same for the trip end
  mutate(trip_end_date_time = paste(substr(trip_end_date, 1, 10), trip_end_time)) %>%
  # change the new column types to a date
  change_to_dates("trip_start_date_time", "%Y-%m-%d %H%M") %>%
  change_to_dates("trip_end_date_time", "%Y-%m-%d %H%M") %>%
  # change the column type to a number
  mutate(reported_quantity = as.integer(reported_quantity))

# view
fhier_logbooks_content %>% dplyr::select(starts_with("trip")) %>% str()

```

#### Fix typos

```{r fix typos }

fhier_logbooks_content_date_fixed_tmp <-
  fhier_logbooks_content %>%
  # if a "trip_end_date" is before 2020 - use "notif_trip_end_date" column instead
  mutate(trip_end_date1 = ifelse(
    trip_end_date < "2020-01-01",
    notif_trip_end_date,
    trip_end_date
  ))

fhier_logbooks_content_date_fixed <-
  fhier_logbooks_content_date_fixed_tmp %>%
  # manually change the wrong value
  mutate(trip_end_date2 = ifelse(
    # find it
    grepl("1992", fhier_logbooks_content_date_fixed_tmp$trip_end_date1),
    # change it
    "2022-10-16 01:00:00",
    # don't change anything else
    trip_end_date1
  ))

```

#### Use only 2022 data

```{r use only 2022 data}
fhier_logbooks_content_date_fixed %<>%
  dplyr::filter(year(trip_end_date) == "2022")
```

### Add waves

```{r wave }

fhier_logbooks_content_waves <-
  fhier_logbooks_content_date_fixed %>%
  # add a new column with a trip end Month
  mutate(end_month = as.yearmon(trip_end_date2)) %>%
  # add a new column with a trip end Year
  mutate(end_year =
           year(trip_end_date2)) %>%
  # add a new column with a number for each trip end Month
  mutate(end_month_num = month(trip_end_date2)) %>%
  # add a new column with a Wave
  mutate(end_wave  = floor((end_month_num + 1) / 2))

```

#### Test fhier_logbooks_content_waves

```{r test fhier_logbooks_content_waves}
#| classes: test

# show the new columns
fhier_logbooks_content_waves %>%
  dplyr::select(end_month, end_year, end_month_num, end_wave) %>%
  unique() %>%
  # sort by end_month_num
  arrange(end_month_num)

```

### FL county to region

```{r FL county to region }

# Florida counties by region (from the Internet)
fl_counties <- list(
  "SA" = c(
    "Brevard",
    "Broward",
    "Duval",
    "Flagler",
    "Indian River",
    "Martin",
    "Miami-Dade",
    "Nassau",
    "Palm Beach",
    "St. Johns",
    "St. Lucie",
    "Volusia"
  ),
  "GOM" = c(
    "Bay",
    "Charlotte",
    "Citrus",
    "Collier",
    "Dixie",
    "Escambia",
    "Franklin",
    "Gulf",
    "Hernando",
    "Hillsborough",
    "Lee",
    "Levy",
    "Manatee",
    "Monroe",
    "Okaloosa",
    "Pasco",
    "Pinellas",
    "Santa Rosa",
    "Sarasota",
    "Taylor",
    "Wakulla",
    "Walton"
  )
)

fhier_logbooks_content_waves_fl_county <-
  fhier_logbooks_content_waves %>%
  # create a new column "end_port_fl_reg" with SA, GOM or whatever else left
  mutate(
    end_port_fl_reg = case_when(
      # check in the list
      fix_names(end_port_county) %in% fix_names(fl_counties$SA) ~ "sa",
      fix_names(end_port_county) %in% fix_names(fl_counties$GOM) ~ "gom",
      # if not on the list - keep it
      .default = end_port_county
    )
  )

```

#### Not GOM or SA fhier_logbooks_content_waves_fl_county

```{r Not GOM or SA fhier_logbooks_content_waves_fl_county }

fhier_logbooks_content_waves_fl_county %>%
  # get FL only
  dplyr::filter(end_port_state == "FL") %>%
  # sort by county
  arrange(end_port_county) %>%
  distinct() %>%
  # 37 counties
  dplyr::select(end_port_fl_reg) %>%
  # what else is in the new column beside sa and gom
  dplyr::filter(!(end_port_fl_reg %in% c("sa", "gom"))) %>% unique()

# NOT-SPECIFIED

```

### States to GOM or SA

```{r States to GOM or SA }

# list of states in the South Atlantic region (from the Internet)
states_sa <- data.frame(
  state_name = c(
    "Delaware",
    "District of Columbia",
    # "Florida", # exclude, we have it separated by county
    "Georgia",
    "Maryland",
    "North Carolina",
    "South Carolina",
    "Virginia",
    "West Virginia"
  )
)

```

#### Get state abbreviations

```{r get abbreviations}
sa_state_abb <-
  # a default R table
  state_tbl %>%
  # get only these in our list
  dplyr::filter(state_name %in% tolower(states_sa$state_name)) %>%
  # get abbreviations
  dplyr::select(state_abb)
```

#### Add sa/gom to states

```{r add sa/gom to states}

fhier_logbooks_content_waves__sa_gom <-
  fhier_logbooks_content_waves_fl_county %>%
  # add a new column "end_port_sa_gom" with sa or gom for each state
  # use fix_name aux function to unify state names (lower case, no spaces etc.)
  mutate(end_port_sa_gom = case_when(
    # if a name is in our SA list - "sa", otherwise - "gom"
    fix_names(end_port_state) %in% fix_names(sa_state_abb$state_abb) ~ "sa",
    .default = "gom"
  )) %>%
  # go through the new column again
  # if an end port state is Florida - use the region from the previous step (column "end_port_fl_reg")
  # otherwise don't change
  mutate(end_port_sa_gom = ifelse(
    tolower(end_port_state) == "fl",
    end_port_fl_reg,
    end_port_sa_gom
  )) %>%
  # remove this column, we don't need it anymore
  dplyr::select(-end_port_fl_reg)
```

#### Test fhier_logbooks_content_waves\_\_sa_gom

```{r test fhier_logbooks_content_waves__sa_gom}
#| classes: test
fhier_logbooks_content_waves__sa_gom %>%
  # look at states and regions
  dplyr::select(end_port_state, end_port_sa_gom) %>%
  unique() %>%
  glimpse()

```

### FHIER quantity by species state region waves

```{r see fhier_logbooks_content_waves__sa_gom }
glimpse(fhier_logbooks_content_waves__sa_gom)
```

```{r fhier quantity by species state region waves }
fhier_catch_by_species_state_region_waves <-  
  fhier_logbooks_content_waves__sa_gom %>%
  # dplyr::select only relevant columns
  dplyr::select(
    catch_species_itis,
    end_port_state,
    end_port_sa_gom,
    end_year,
    end_wave,
    reported_quantity
  ) %>%
  # group by all of them but "reported_quantity"
  group_by(
    catch_species_itis,
    end_port_state,
    end_port_sa_gom,
    end_year,
    end_wave
  ) %>%
  # save a sum of reported_quantity in each group in fhier_quantity_by_4
  # remove NAs
  summarise(fhier_quantity_by_4 = sum(as.integer(reported_quantity), na.rm = TRUE)) %>%
  as.data.frame()

```

##### Test numbers

```{r test numbers}
#| classes: test

fhier_catch_by_species_state_region_waves %>%
  # get the same species
  dplyr::filter(catch_species_itis == "167687") %>%
  # group by region
  group_by(catch_species_itis, end_port_sa_gom) %>%
  # sum the FHIER catch
  summarise(bass_fhier_cnt = sum(fhier_quantity_by_4, na.rm = TRUE))
```

## MRIP data

### Convert ab1 to integers

```{r convert ab1 to integers }
mrip_estimate %<>%
  mutate(ab1 = as.integer(ab1))

```

### MRIP estimate catch by species state region waves

```{r mrip estimate catch by species state region waves}

mrip_estimate_catch_by_species_state_region_waves <-
  mrip_estimate %>%
  # dplyr::select the relevan columns only
  dplyr::select(itis_code, new_sta, sub_reg, year, wave, ab1) %>%
  # group by all except the counts
  group_by(itis_code, new_sta, sub_reg, year, wave) %>%
  # save the sum of "ab1" for each group in "mrip_estimate_catch_by_4"
  # remove NAs
  summarise(mrip_estimate_catch_by_4 = sum(as.integer(ab1), na.rm = TRUE)) %>%
  as.data.frame()

glimpse(mrip_estimate_catch_by_species_state_region_waves)
# 'data.frame':	878 obs. of  6 variables

```

#### Change columns type

```{r change clmn type}
# "year" and "wave" to numbers
mrip_estimate_catch_by_species_state_region_waves1 <-
  mrip_estimate_catch_by_species_state_region_waves %>%
  mutate(year = as.double(year)) %>%
  mutate(wave = as.double(wave))
```

#### Change sa_gom MRIP to char

```{r change sa_gom mrip to char}
mrip_estimate_catch_by_species_state_region_waves <-
  mrip_estimate_catch_by_species_state_region_waves1 %>%
  # change a 6 to "sa" and a 7 "gom", leave everything else in place
  mutate(sa_gom = case_when(sub_reg == "6" ~ "sa",
                            sub_reg == "7" ~ "gom",
                            .default = sub_reg),
                            # put the new column after sub_reg (by default at the end)
                            .after = sub_reg) %>%
  # drop sub_reg
  dplyr::select(-sub_reg)

```

# Compare FHIER with MRIP

## Combine wave data for fhier and mrip

#### Rename fields

```{r rename fields}

# common field names
wave_data_names_common <- c("species_itis",
                     "state",
                     "sa_gom",
                     "year",
                     "wave"
                    )

# to be sure columns are in the same order
names(mrip_estimate_catch_by_species_state_region_waves)

# mrip_names <- c("itis_code",
#                 "new_sta",
#                 "sa_gom",
#                 "year",
#                 "wave",
#                 "mrip_estimate_catch_by_4"
# )

# specific names
wave_data_names_f <- c(wave_data_names_common, c("fhier_catch_by_4"))
wave_data_names_m <- c(wave_data_names_common, c("mrip_estimate_catch_by_4"))

# change names
names(fhier_catch_by_species_state_region_waves) <- wave_data_names_f
names(mrip_estimate_catch_by_species_state_region_waves) <- wave_data_names_m

# identical(names(fhier_catch_by_species_state_region_waves)[1:5],
          # names(mrip_estimate_catch_by_species_state_region_waves)[1:5])
```

#### Join FHIER and MRIP data

```{r join FHIER and MRIP data}
fhier_mrip_catch_by_species_state_region_waves <-
  full_join(fhier_catch_by_species_state_region_waves,
             mrip_estimate_catch_by_species_state_region_waves,
              by = join_by(species_itis, state, sa_gom, year, wave)
             )
# default Joining with `by = join_by(species_itis, state, sa_gom, year, wave)`
# final$S1 <- dplyr::coalesce(final[[" S1 .x"]],  final[[" S1 .y"]])

# look at the first 20 entries for Black see bass
fhier_mrip_catch_by_species_state_region_waves %>%
  dplyr::filter(species_itis == "167687") %>% head(20)

```

##### Test numbers MRIP

```{r test numbers MRIP}
#| classes: test
mrip_estimate_catch_by_species_state_region_waves %>%
  # get one species
  dplyr::filter(species_itis == "167687") %>%
  # group by region
  group_by(species_itis, sa_gom) %>%
  # sum the MRIP catch
  summarise(bass_mrip_cnt = sum(mrip_estimate_catch_by_4, na.rm = TRUE))
```

##### Test numbers FHIER

```{r test numbers FHIER}
#| classes: test

fhier_catch_by_species_state_region_waves %>%
  # get the same species
  dplyr::filter(species_itis == "167687") %>%
  # group by region
  group_by(species_itis, sa_gom) %>%
  # sum the FHIER catch
  summarise(bass_fhier_cnt = sum(fhier_catch_by_4, na.rm = TRUE))
```

#### Test numbers in the join

```{r test numbers in the join}
#| classes: test

# compare the above numbers with those in the join, they should be the same
fhier_mrip_catch_by_species_state_region_waves %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis, sa_gom) %>%
  summarise(bass_fhier_cnt = sum(fhier_catch_by_4, na.rm = TRUE))

fhier_mrip_catch_by_species_state_region_waves %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis, sa_gom) %>%
  summarise(bass_mrip_cnt = sum(mrip_estimate_catch_by_4, na.rm = TRUE))

```

## Make a FHIER common_name df

```{r make a common_name df}

# dplyr::select common names and itis in a separate data frame
fhier_common_names <-
  fhier_logbooks_content %>%
  # names()
  dplyr::select(catch_species_itis, common_name) %>%
  unique()

# add column names
names(fhier_common_names) <- c("species_itis", "common_name")

```

## list of 10 spp
```{r list of 10 spp sa}
sa_10 <- c(
"GROUPER, RED",
"SNAPPER, RED",
"TRIGGERFISH, GRAY",
"GROUPER, SCAMP",
"BASS, BLACK SEA",
"MACKEREL, SPANISH",
"TILEFISH",
"TILEFISH, BLUE",
"GROUPER, GAG",
"DOLPHIN MAHI")
```

```{r top 10 sa counts}
sa_10_spp <-
  fhier_common_names %>%
  dplyr::filter(common_name %in% sa_10)

View(sa_10_spp)
# intersect(sa_10, fhier_common_names$common_name)

```


```{r list of 10 spp gom}
gom_10 <- c(
"GROUPER, RED",
"SNAPPER, RED",
"TRIGGERFISH, GRAY",
"GROUPER, SCAMP",
"SNAPPER, GRAY",
"MACKEREL, SPANISH",
"MACKEREL, KING",
"COBIA",
"AMBERJACK, GREATER",
"GROUPER, GAG",
"TILEFISHES")
```


```{r list of 10 spp gom cnts}
gom_10_spp <-
  fhier_common_names %>%
  dplyr::filter(common_name %in% gom_10)

View(gom_10_spp)
  
```


## One plot function

```{r one plot function}

# A function to make a plot by spp.
plot_by_spp <- function(com_name, my_df, no_legend = TRUE) {
  # browser()

 one_plot <-
  my_df %>%
    # only the com name from the parameters
    dplyr::filter(common_name == !!com_name) %>%
  ggplot(
         aes(x = year_wave,
             y = CATCH_CNT,
            # color by the agency and
            # make a legend if no_legend is FALSE
             fill = AGENCY)
  ) +
    # manually cange default colours
    scale_fill_manual(values = c("MRIP" = "deepskyblue", "FHIER" = "red")) +
    # columns are side by side (not stacked)
    geom_col(position = "dodge") +
    labs(title = com_name,
        # remove x and y axes titles
         x = "",
         y = ""
    ) +
   theme(
    # turn x text
      axis.text.x = element_text(angle = 45),
    # change text size
      plot.title = element_text(size = 9),
      legend.title = element_text(size = 8),
      legend.text = element_text(size = 8)
   )

  # By default the "no_legend" parameter is TRUE
 if (no_legend) {
    one_plot <- one_plot +
      theme(legend.position = "none")
  }
  return(one_plot)
}

```

## Prepare data for ploting

#### glimpse(fhier_mrip_catch_by_species_state_region_waves)

```{r glimpse(fhier_mrip_catch_by_species_state_region_waves) }

glimpse(fhier_mrip_catch_by_species_state_region_waves)
# Rows: 6,327
# Columns: 7
# ?Rows: 5,728


```

#### Combine year and wave

```{r combine year_wave}

# make a new column "year_wave"
fhier_mrip_catch_by_species_state_region_waves_tmp1 <-
  mutate(fhier_mrip_catch_by_species_state_region_waves,
         year_wave = paste(year, wave, sep = "_"))

```

#### Add common_names

```{r add common_names}

# Add the fhier_common_names we made earlier
fhier_mrip_catch_by_species_state_region_waves_tmp2 <-
  inner_join(fhier_mrip_catch_by_species_state_region_waves_tmp1,
           fhier_common_names,
           by = join_by(species_itis))
```

#### Split by sa_gom column

```{r split by sa_gom column}
#| warning: false

# Make separate data frames
fhier_mrip_catch_by_species_state_region_waves_list_for_plot <-
  fhier_mrip_catch_by_species_state_region_waves_tmp2 %>%
  # split by sa_gom column
    split(as.factor(fhier_mrip_catch_by_species_state_region_waves$sa_gom)) %>%
  # remove extra columns in each df
    map(
      .f = list(. %>% dplyr::select(-one_of("year", "wave", "sa_gom")
                                    )
                )
  )

glimpse(fhier_mrip_catch_by_species_state_region_waves_list_for_plot)

```

#### Test numbers in the list

```{r test numbers in the list}
#| classes: test

# For each region sum counts for one species,
# should be the same as before

# GOM
fhier_mrip_catch_by_species_state_region_waves_list_for_plot$gom %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_fhier_cnt = sum(fhier_catch_by_4, na.rm = TRUE))

# SA
fhier_mrip_catch_by_species_state_region_waves_list_for_plot$sa %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_fhier_cnt = sum(mrip_estimate_catch_by_4, na.rm = TRUE))

```

### Add top ten info back

```{r add top ten info}

# keep only entries for spp. in the top ten list,
# separately for each region
fhier_mrip_catch_by_species_state_region_waves_list_for_plot_gom10 <-
  fhier_mrip_catch_by_species_state_region_waves_list_for_plot$gom %>%
  dplyr::filter(species_itis %in% gom_10_spp$species_itis)
# 231  
# dplyr::filter(species_itis %in% n_most_frequent_fhier_10_list$gom$species_itis)
# Rows: 217
# str(fhier_mrip_catch_by_species_state_region_waves_list_for_plot_gom10)
# ?'data.frame':	196 obs. of  6 variables

fhier_mrip_catch_by_species_state_region_waves_list_for_plot_sa10 <-
  fhier_mrip_catch_by_species_state_region_waves_list_for_plot$sa %>%
  dplyr::filter(species_itis %in% sa_10_spp$species_itis)
  # dplyr::filter(species_itis %in% n_most_frequent_fhier_10_list$sa$species_itis)

glimpse(fhier_mrip_catch_by_species_state_region_waves_list_for_plot_sa10)
# Rows: 300
# Rows: 274
# 173


```

### Test numbers in the list by sa_gom

```{r test numbers in the list by sa_gom}
#| classes: test

# For the top 10, for each region sum separately MRIP and FHIER counts for one species,
# should be the same as before

# SA, FHIER counts
fhier_mrip_catch_by_species_state_region_waves_list_for_plot_sa10 %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_fhier_cnt = sum(fhier_catch_by_4, na.rm = TRUE))

# GOM, FHIER counts
fhier_mrip_catch_by_species_state_region_waves_list_for_plot_gom10 %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_fhier_cnt = sum(fhier_catch_by_4, na.rm = TRUE))

# SA, MRIP counts
fhier_mrip_catch_by_species_state_region_waves_list_for_plot_sa10 %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_fhier_cnt = sum(mrip_estimate_catch_by_4, na.rm = TRUE))

# GOM, MRIP counts
fhier_mrip_catch_by_species_state_region_waves_list_for_plot_gom10 %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_fhier_cnt = sum(mrip_estimate_catch_by_4, na.rm = TRUE))

# numbers OK
```

## GOM plots

#### Pivot_longer fhier_mrip_catch_by_species_state_region_waves_list_for_plot_gom

```{r pivot_longer}
fhier_mrip_gom_to_plot <-
  fhier_mrip_catch_by_species_state_region_waves_list_for_plot_gom10 %>%
  # change to shorter column names
  rename(c("MRIP" = "mrip_estimate_catch_by_4",
           "FHIER" = "fhier_catch_by_4")) %>%
  # reformat to a long format to have fhier and mrip data side by side
  pivot_longer(
    cols = c(MRIP,
             FHIER),
    names_to = "AGENCY",
    values_to = "CATCH_CNT"
  ) %>%
  # use only the new columns
  dplyr::select(year_wave, species_itis, common_name, AGENCY, CATCH_CNT) %>%
  # remove lines where one or another agency doesn't have counts for this species
  drop_na()

glimpse(fhier_mrip_gom_to_plot)
```

### Simple plot GOM

```{r gom simple plot}

# an overview plot
plot(fhier_mrip_gom_to_plot)

```

### GOM plots for top spp.

```{r 10 gom plots}
# plot_by_spp("BASS, BLACK SEA", fhier_mrip_gom_to_plot)

           # for each common name from the top 10
plots10 <- map(unique(fhier_mrip_gom_to_plot$common_name),
              # run the plot_by_spp with this common name as a parameter and the default value for no_legend (TRUE)
               function(x) {plot_by_spp(x, fhier_mrip_gom_to_plot)}
               )

# Title for all plots together
super_title = "GOM: The top 9 most abundant FHIER species by waves"

# separate a legend
plot_w_legend <- plot_by_spp("BASS, BLACK SEA",
                             fhier_mrip_gom_to_plot,
                             # keep the legend
                             FALSE)
# use an aux function to pull out the legend
my_legend <- legend_for_grid_arrange(plot_w_legend)

# combine all plots
grid.arrange(grobs = plots10,
             top = super_title,
             left = my_legend,
             ncol = 3)

```

## SA plots

#### Pivot_longer fhier_mrip_catch_by_species_state_region_waves_list_for_plot_sa

```{r sa pivot_longer}
fhier_mrip_sa_to_plot <-
  fhier_mrip_catch_by_species_state_region_waves_list_for_plot_sa10 %>%
  # rename to shorter column names
  rename(c("MRIP" = "mrip_estimate_catch_by_4",
           "FHIER" = "fhier_catch_by_4")) %>%
  # reformat to a long format to have fhier and mrip data side by side
  pivot_longer(
    cols = c(MRIP,
             FHIER),
    names_to = "AGENCY",
    values_to = "CATCH_CNT"
  ) %>%
  # use only the new columns
  dplyr::select(year_wave, species_itis, common_name, AGENCY, CATCH_CNT) %>%
  # remove lines where one or another agency doesn't have counts for this species
  drop_na()

glimpse(fhier_mrip_sa_to_plot)
```

### Simple plot SA

```{r sa simple plot}
# An overview plot
plot(fhier_mrip_sa_to_plot)

```

### SA plots for top spp.

```{r 10 sa plots}

           # for each common name from the top 10
plots10 <- map(unique(fhier_mrip_sa_to_plot$common_name),
              # run the plot_by_spp with this common name as a parameter and the default value for no_legend (TRUE)
               function(x) {plot_by_spp(x, fhier_mrip_sa_to_plot)}
               )

# The following code is the same as before, with "SA" instead of "GOM"
super_title = "SA: The top 9 most abundant FHIER species by waves"

# separate a legend
plot_w_legend <- plot_by_spp("BASS, BLACK SEA", fhier_mrip_sa_to_plot, FALSE)
my_legend <- legend_for_grid_arrange(plot_w_legend)

grid.arrange(grobs = plots10,
             top = super_title,
             left = my_legend,
             ncol = 3)

```

## Not NAs only

#### Overview

```{r Overview}
dim(fhier_mrip_catch_by_species_state_region_waves)
# [1] 5728    7

fhier_mrip_catch_by_species_state_region_waves_no_na <-
fhier_mrip_catch_by_species_state_region_waves %>%
  dplyr::filter(complete.cases(.))
# 'data.frame':	786 obs. of  7 variables:

# fhier_mrip_catch_by_species_state_region_waves %>% 
#   tidyr::drop_na(mrip_estimate_catch_by_4,
#                  # 878 obs. of  7 variables
#                  fhier_catch_by_4) %>% str()
# 786 obs. of  7 variables


```

## No NAs: Get 10 most frequent spp. by region

### split no NAs by region for top 10

```{r split no NAs by region}
fhier_mrip_catch_by_species_state_region_waves_no_na_list <-
  fhier_mrip_catch_by_species_state_region_waves_no_na %>%
  # split by sa/gom
    split(as.factor(fhier_mrip_catch_by_species_state_region_waves_no_na$sa_gom))

```

### No NAs Get 10 most frequent spp.

```{r No NAs Get 10 most frequent spp. by region}

# Look at the top most frequent FHIER spp. for each region
n_most_frequent_fhier_10_list_no_na <-
  fhier_mrip_catch_by_species_state_region_waves_no_na_list %>%
  # repeat for each region (SA and GOM)
  map(function(x) {x %>%
      # dplyr::select ITIS and counts
      dplyr::select(species_itis, fhier_catch_by_4) %>%
      group_by(species_itis) %>%
      # add a new column with a sum of counts for each spp.
      summarise(fhier_catch_by_spp = sum(fhier_catch_by_4, na.rm = TRUE)) %>%
      # sort in the discending order
      arrange(desc(fhier_catch_by_spp)) %>%
      # get the top 10
      head(10)
})
```

#### No NAs 10 most frequent spp. GOM

```{r No NAs 10 most frequent spp. GOM}
n_most_frequent_fhier_10_list_no_na$gom
```

#### No NAs 10 most frequent spp. SA

```{r No NAs 10 most frequent spp. SA}
n_most_frequent_fhier_10_list_no_na$sa

```

## No NAs prepare data for plotting

### No NAs Combine year and wave

```{r No NAs combine year_wave}
# Use fhier_mrip_catch_by_species_state_region_waves_no_na again
# make a new column "year_wave"
fhier_mrip_catch_by_species_state_region_waves_no_na_tmp1 <-
  mutate(fhier_mrip_catch_by_species_state_region_waves_no_na,
         year_wave = paste(year, wave, sep = "_"))

```

### No NAs Add common_names

```{r No NAs add common_names}

# Add the fhier_common_names we made earlier
fhier_mrip_catch_by_species_state_region_waves_no_na_tmp2 <-
  inner_join(fhier_mrip_catch_by_species_state_region_waves_no_na_tmp1,
           fhier_common_names,
           by = join_by(species_itis))
```

### No NAs Split by sa_gom column to plot

```{r No NAs split by sa_gom column to plot}
#| warning: false

# Make separate data frames
fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot <-
  fhier_mrip_catch_by_species_state_region_waves_no_na_tmp2 %>%
  # split by sa_gom column
    split(as.factor(fhier_mrip_catch_by_species_state_region_waves_no_na$sa_gom)) %>%
  # remove extra columns in each df
    map(
      .f = list(. %>% dplyr::select(-one_of("year", "wave", "sa_gom")
                                    )
                )
  )

glimpse(fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot)

fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$sa %>%
  dplyr::select(species_itis) %>% unique()
# 58
n_most_frequent_fhier_10_list_no_na$sa
setdiff(n_most_frequent_fhier_10_list_no_na$sa$species_itis,
        fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$sa$species_itis)
# 0

setdiff(fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$sa$species_itis,
        n_most_frequent_fhier_10_list_no_na$sa$species_itis
        )
# 48

tmp1 <-
inner_join(fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$sa,
        n_most_frequent_fhier_10_list_no_na$sa)

tmp1 %>%
  dplyr::select(species_itis) %>% unique()
# 10

```

#### No NAs Test numbers in the list

```{r No NAs test numbers in the list}
#| classes: test

# For each region sum counts for one species,
# should be the same as before

# GOM
fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$gom %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_gom_fhier_cnt = sum(fhier_catch_by_4, na.rm = TRUE),
            bass_gom_mrip_cnt = sum(mrip_estimate_catch_by_4, na.rm = TRUE)
            )

# SA
fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$sa %>%
  dplyr::filter(species_itis == "167687") %>%
  group_by(species_itis) %>%
  summarise(bass_sa_fhier_cnt = sum(fhier_catch_by_4, na.rm = TRUE),
            bass_sa_mrip_cnt = sum(mrip_estimate_catch_by_4, na.rm = TRUE)
            )
```

### No NAs Add top ten info back

```{r No NAs add top ten info}

# keep only entries for spp. in the top ten list,
# separately for each region
fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot_gom10 <-
  fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$gom %>%
  dplyr::filter(species_itis %in% n_most_frequent_fhier_10_list_no_na$gom$species_itis)

glimpse(fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot_gom10)
# 109 obs. of  6 variables

fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot_sa10 <-
  fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot$sa %>%
  dplyr::filter(species_itis %in% n_most_frequent_fhier_10_list_no_na$sa$species_itis)

glimpse(fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot_sa10)
# Rows: 140


```

## No NAs No NAs GOM plots

#### No NAs Pivot_longer

```{r No NAs pivot_longer}
fhier_mrip_gom__no_na_to_plot <-
  fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot_gom10 %>%
  # change to shorter column names
  rename(c("MRIP" = "mrip_estimate_catch_by_4",
           "FHIER" = "fhier_catch_by_4")) %>%
  # reformat to a long format to have fhier and mrip data side by side
  pivot_longer(
    cols = c(MRIP,
             FHIER),
    names_to = "AGENCY",
    values_to = "CATCH_CNT"
  ) %>%
  # use only the new columns
  dplyr::select(year_wave, species_itis, common_name, AGENCY, CATCH_CNT) %>%
  # remove lines where one or another agency doesn't have counts for this species
  drop_na()

glimpse(fhier_mrip_gom__no_na_to_plot)

# fhier_mrip_gom__no_na_to_plot %>% dplyr::select(species_itis) %>% unique()
# 10
```

### No NAs Simple plot GOM

```{r No NAs gom simple plot}

# an overview plot
plot(fhier_mrip_gom__no_na_to_plot)

```

### No NAs GOM plots for top spp.

```{r No NAs 10 gom plots}
# plot_by_spp("BASS, BLACK SEA", fhier_mrip_gom__no_na_to_plot)
# fhier_mrip_gom__no_na_to_plot %>%
#   dplyr::select(common_name) %>% unique()
# 10

           # for each common name from the top 10
plots10 <- map(unique(fhier_mrip_gom__no_na_to_plot$common_name),
              # run the plot_by_spp with this common name as a parameter and the default value for no_legend (TRUE)
               function(x) {plot_by_spp(x, fhier_mrip_gom__no_na_to_plot)}
               )

# Title for all plots together
super_title = "GOM: The top 10 most abundant FHIER species by waves, no NAs"

# separate a legend
plot_w_legend <- plot_by_spp("BASS, BLACK SEA",
                             fhier_mrip_gom__no_na_to_plot,
                             # keep the legend
                             FALSE)
# use an aux function to pull out the legend
my_legend <- legend_for_grid_arrange(plot_w_legend)

# combine all plots
grid.arrange(grobs = plots10,
             top = super_title,
             left = my_legend,
             ncol = 3)

```

## No NAs SA plots

#### No NAs Pivot_longer fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot_sa

```{r No NAs sa pivot_longer}
fhier_mrip_sa__no_na_to_plot <-
  fhier_mrip_catch_by_species_state_region_waves_no_na_for_plot_sa10 %>%
  # rename to shorter column names
  rename(c("MRIP" = "mrip_estimate_catch_by_4",
           "FHIER" = "fhier_catch_by_4")) %>%
  # reformat to a long format to have fhier and mrip data side by side
  pivot_longer(
    cols = c(MRIP,
             FHIER),
    names_to = "AGENCY",
    values_to = "CATCH_CNT"
  ) %>%
  # use only the new columns
  dplyr::select(year_wave, species_itis, common_name, AGENCY, CATCH_CNT) %>%
  # remove lines where one or another agency doesn't have counts for this species
  drop_na()

glimpse(fhier_mrip_sa__no_na_to_plot)
# fhier_mrip_sa__no_na_to_plot %>%
#   dplyr::select(species_itis) %>% unique()
# 10

```

### No NAs Simple plot SA

```{r No NAs sa simple plot}
# An overview plot
plot(fhier_mrip_sa__no_na_to_plot)

```

### No NAs SA plots for top spp.

```{r No NAs 10 sa plots}

           # for each common name from the top 10
plots10 <- map(unique(fhier_mrip_sa__no_na_to_plot$common_name),
              # run the plot_by_spp with this common name as a parameter and the default value for no_legend (TRUE)
               function(x) {plot_by_spp(x, fhier_mrip_sa__no_na_to_plot)}
               )

# The following code is the same as before, with "SA" instead of "GOM"
super_title = "SA: The top 10 most abundant FHIER species by waves, no NAs"

# separate a legend
plot_w_legend <- plot_by_spp("BASS, BLACK SEA", fhier_mrip_sa__no_na_to_plot, FALSE)
my_legend <- legend_for_grid_arrange(plot_w_legend)

grid.arrange(grobs = plots10,
             top = super_title,
             left = my_legend,
             ncol = 3)

```
