---
title: "compare_catch"
date: 2023-04-03
output:
  html_document
format:
  html:
    css: styles.css
    code-overflow: wrap
---

Compare catch in survey vs logbook
see read.me

```{r no cache setup, include=FALSE}
#| echo: false
library(zoo)

source("~/R_code_github/useful_functions_module.r")
my_paths <- set_work_dir()
```

```{r setup, cache=TRUE, include=FALSE}
#| echo: false

source("~/R_code_github/compare_catch/get_data.R")

```

## FHIER data

## get field names
```{r logbooks_content }
itis_field_name <- grep("itis", names(logbooks_content), value = T)
# catch_species_itis

vessel_id_field_name <-
  grep("vessel.*official", names(logbooks_content), value = T)
# vessel_official_nbr

```

### clean logbooks_content
```{r clean logbooks_content }

fhier_logbooks_content <-
  logbooks_content  %>%
  mutate(trip_start_date_time = paste(substr(trip_start_date, 1, 10), trip_start_time)) %>%
  mutate(trip_end_date_time = paste(substr(trip_end_date, 1, 10), trip_end_time)) %>%
  change_to_dates("trip_start_date_time", "%Y-%m-%d %H%M") %>%
  change_to_dates("trip_end_date_time", "%Y-%m-%d %H%M") %>%
  mutate(reported_quantity = as.integer(reported_quantity))

# rm(logbooks_content)
# gc()
fhier_logbooks_content %>% select(starts_with("trip")) %>% str()

```

#### fix typos
```{r fix typos }

fhier_logbooks_content_date_fixed_tmp <-
  fhier_logbooks_content %>%
  mutate(trip_end_date1 = ifelse(
    trip_end_date < "2020-01-01",
    notif_trip_end_date,
    trip_end_date
  ))

# grep("1992", fhier_logbooks_content_date_fixed_tmp$trip_end_date1, value = T)

fhier_logbooks_content_date_fixed <-
  fhier_logbooks_content_date_fixed_tmp %>%
  mutate(trip_end_date2 = ifelse(
    grepl("1992", fhier_logbooks_content_date_fixed_tmp$trip_end_date1),
    "2022-10-16 01:00:00",
    trip_end_date1
  ))

```

### Add waves
```{r wave }

fhier_logbooks_content_waves <-
  fhier_logbooks_content_date_fixed %>%
  mutate(end_month = as.yearmon(trip_end_date2)) %>%
  mutate(end_year =
           year(trip_end_date2)) %>%
  mutate(end_month_num = month(trip_end_date2)) %>%
  mutate(end_wave  = floor((end_month_num + 1) / 2))

```

#### test fhier_logbooks_content_waves
```{r test fhier_logbooks_content_waves}

fhier_logbooks_content_waves %>%
  select(end_month, end_year, end_month_num, end_wave) %>%
  unique() %>%
  arrange(end_month_num)

```

### FL county to region
```{r FL county to region }
fl_counties <- list(
  "SA" = c(
    "Brevard",
    "Broward",
    "Duval",
    "Flagler",
    "Indian River",
    "Martin",
    "Miami-Dade",
    "Nassau",
    "Palm Beach",
    "St. Johns",
    "St. Lucie",
    "Volusia"
  ),
  "GOM" = c(
    "Bay",
    "Charlotte",
    "Citrus",
    "Collier",
    "Dixie",
    "Escambia",
    "Franklin",
    "Gulf",
    "Hernando",
    "Hillsborough",
    "Lee",
    "Levy",
    "Manatee",
    "Monroe",
    "Okaloosa",
    "Pasco",
    "Pinellas",
    "Santa Rosa",
    "Sarasota",
    "Taylor",
    "Wakulla",
    "Walton"
  )
)

# str(fl_counties)
fhier_logbooks_content_waves_fl_county <-
  fhier_logbooks_content_waves %>%
  mutate(
    end_port_fl_reg = case_when(
      fix_names(end_port_county) %in% fix_names(fl_counties$SA) ~ "sa",
      fix_names(end_port_county) %in% fix_names(fl_counties$GOM) ~ "gom",
      .default = end_port_county
    )
  )

```

#### test fhier_logbooks_content_waves_fl_county
```{r test fhier_logbooks_content_waves_fl_county }
fhier_logbooks_content_waves_fl_county %>%
  filter(end_port_state == "FL") %>%
  arrange(end_port_county) %>%
  distinct() %>%
  # 37
  select(end_port_fl_reg) %>%
  filter(!(end_port_fl_reg %in% c("sa", "gom"))) %>% unique()

# NOT-SPECIFIED

```

### States to GOM or SA
```{r States to GOM or SA }

states_sa <- data.frame(
  state_name = c(
    "Delaware",
    "District of Columbia",
    # "Florida",
    "Georgia",
    "Maryland",
    "North Carolina",
    "South Carolina",
    "Virginia",
    "West Virginia"
  )
)

```


#### get abbreviations
```{r get abbreviations}
sa_state_abb <-
  state_tbl %>%
  filter(state_name %in% tolower(states_sa$state_name)) %>%
  select(state_abb)
```

#### add sa/gom to states
```{r add sa/gom to states}

fhier_logbooks_content_waves__sa_gom <-
  fhier_logbooks_content_waves_fl_county %>%
  mutate(end_port_sa_gom = case_when(
    fix_names(end_port_state) %in% fix_names(sa_state_abb$state_abb) ~ "sa",
    .default = "gom"
  )) %>%
  mutate(end_port_sa_gom = ifelse(
    tolower(end_port_state) == "fl",
    end_port_fl_reg,
    end_port_sa_gom
  )) %>%
  select(-end_port_fl_reg)
```

#### test fhier_logbooks_content_waves__sa_gom
```{r test fhier_logbooks_content_waves__sa_gom}

fhier_logbooks_content_waves__sa_gom %>%
  select(end_port_state, end_port_sa_gom) %>%
  unique() %>%
  glimpse()

# names(fhier_logbooks_content_waves__sa_gom) %>% cat()

```

### fhier_quantity_by_species_permit_state_region_waves
```{r fhier_quantity_by_species_permit_state_region_waves }
glimpse(fhier_logbooks_content_waves__sa_gom)

fhier_catch_by_species_state_region_waves <-
  fhier_logbooks_content_waves__sa_gom %>%
  select(
    catch_species_itis,
    common_name,
    end_port_state,
    end_port_sa_gom,
    end_year,
    end_wave,
    reported_quantity
  ) %>%
  group_by(
    catch_species_itis,
    common_name,
    end_port_state,
    end_port_sa_gom,
    end_year,
    end_wave
  ) %>%
  summarise(fhier_quantity_by_4 = sum(as.integer(reported_quantity))) %>%
  as.data.frame()
# plot(fhier_catch_by_species_state_region_waves)

fhier_logbooks_content_waves__sa_gom %>% filter(common_name == "BASS, BLACK SEA") %>% group_by(catch_species_itis, end_port_sa_gom) %>% summarise(bass_cnt = sum(reported_quantity))
# A tibble: 2 × 3
# Groups:   catch_species_itis [1]
#   catch_species_itis end_port_sa_gom     ff
#   <chr>              <chr>            <int>
# 1 167687             gom              75900
# 2 167687             sa              194054

```

### non specified region in FHIER
```{r non specified region in FHIER }
# gom
# sa
# NOT-SPECIFIED

# fhier_catch_by_species_region %>%
#   filter(sa_gom == "NOT-SPECIFIED")

```

## MRIP data

### convert ab1 to integers
```{r convert ab1 to integers }
# names(mrip_estimate)
mrip_estimate %<>%
  mutate(ab1 = as.integer(ab1))

```

### mrip_estimate_catch_by_species_state_region_waves
```{r mrip_estimate_catch_by_species_state_region_waves}
# glimpse(mrip_estimate)
mrip_estimate_catch_by_species_state_region_waves <-
  mrip_estimate %>%
  select(itis_code, new_com, new_sta, sub_reg, year, wave, ab1) %>%
  group_by(itis_code, new_com, new_sta, sub_reg, year, wave) %>%
  summarise(mrip_estimate_catch_by_4 = sum(as.integer(ab1))) %>%
  as.data.frame()

str(mrip_estimate_catch_by_species_state_region_waves)
# 'data.frame':	878 obs. of  6 variables

mrip_estimate_catch_by_species_state_region_waves %>%
  filter(new_com == "black sea bass") %>%
  group_by(itis_code, sub_reg) %>%
  summarise(bass_mrip_cnt = sum(mrip_estimate_catch_by_4))

# itis_code sub_reg bass_mrip_cnt
# <chr>     <chr>           <int>
# 167687    6               18828
# 167687    7                6708


```

## compare fhier with mrip

#### column names
```{r column names }
sp_itis_fhier <-
  grep("itis", tolower(names(fhier_species_count_by_disposition)), value = TRUE)
sp_itis_mrip <-
  grep("itis", tolower(names(mrip_estimate)), value = TRUE)

```

## combine wave data for fhier and mrip
#### rename fields
```{r rename fields}

wave_data_names_common <- c("species_itis",
                     "common_name",
                     "state",
                     "sa_gom",
                     "year",
                     "wave"
                    ) 

wave_data_names_f <- c(wave_data_names_common, c("fhier_catch_by_4"))
wave_data_names_m <- c(wave_data_names_common, c("mrip_estimate_catch_by_4"))

names(fhier_catch_by_species_state_region_waves) <- wave_data_names_f
names(mrip_estimate_catch_by_species_state_region_waves) <- wave_data_names_m
```

#### change columns type
```{r change clmn type}
mrip_estimate_catch_by_species_state_region_waves1 <-
  mrip_estimate_catch_by_species_state_region_waves %>%
  mutate(year = as.double(year)) %>%
  mutate(wave = as.double(wave))
```

#### change sa_gom mrip to char
```{r}
mrip_estimate_catch_by_species_state_region_waves2 <-
  mrip_estimate_catch_by_species_state_region_waves1 %>%
  mutate(sa_gom = case_when(sa_gom == "6" ~ "sa",
                            sa_gom == "7" ~ "gom",
                            .default = sa_gom))

```

#### join FHIER and MRIP data
```{r join FHIER and MRIP data}
fhier_mrip_catch_by_species_state_region_waves <-
  full_join(fhier_catch_by_species_state_region_waves,
             mrip_estimate_catch_by_species_state_region_waves2,
             # specify fields to exclude "common_name"
             by = join_by(species_itis, state, sa_gom, year, wave)
             )
# Joining with `by = join_by(species_itis, common_name, state, sa_gom, year, wave)`

fhier_mrip_catch_by_species_state_region_waves %>%
  filter(species_itis == "167687") 

```

##### test numbers MRIP
```{r test numbers MRIP}

mrip_estimate_catch_by_species_state_region_waves %>%
  filter(species_itis == "167687") %>%
  group_by(species_itis, sa_gom) %>%
  summarise(bass_mrip_cnt = sum(mrip_estimate_catch_by_4))
```

##### test numbers FHIER
```{r test numbers FHIER}

fhier_catch_by_species_state_region_waves %>%
  filter(species_itis == "167687") %>%
  group_by(species_itis, sa_gom) %>%
  summarise(bass_fhier_cnt = sum(fhier_catch_by_4))
```

```{r test numbers in the join}
fhier_mrip_catch_by_species_state_region_waves %>%
  filter(species_itis == "167687") %>%
  group_by(species_itis, sa_gom) %>%
  summarise(bass_fhier_cnt = sum(fhier_catch_by_4),
            bass_mrip_cnt = sum(mrip_estimate_catch_by_4))
# wrong, no mrip cnts?!

```

## Prepare data for ploting
```{r Prepare data for ploting }

# View(mrip_estimate_catch_by_species_state_region_waves)
mrip_estimate_catch_by_species_state_region_waves <-
  mrip_estimate_catch_by_species_state_region_waves1 %>%
  mutate(sa_gom = case_when(sa_gom == 6 ~ "sa",
                            sa_gom == 7 ~ "gom",
                            .default = sa_gom))

# head(fhier_catch_by_species_state_region_waves)
## join by specieas that are in MRIP, bc that list is shorter
fhier_mrip_catch_by_species_state_region_waves <-
  right_join(fhier_catch_by_species_state_region_waves,
             mrip_estimate_catch_by_species_state_region_waves,
             # has to specify fields here, bc otherwise it will use the "common_name" field too, which is different in the 2 sets
             by = join_by(species_itis, state, sa_gom, year, wave)
  )
# Joining with `by = join_by(species_itis, common_name, state, sa_gom, year, wave)`

# View(fhier_mrip_catch_by_species_state_region_waves)
# 878

```


#### choose fewer columns, combine year_wave, split by sa_gom column into 2

```{r choose fewer columns}

fhier_mrip_catch_by_species_state_region_waves_sa_gom_list_tmp <-
  fhier_mrip_catch_by_species_state_region_waves %>%
  select(
    species_itis,
    state,
    sa_gom,
    year,
    wave,
    common_name.x,
    fhier_catch_by_4,
    mrip_estimate_catch_by_4
  ) %>%
  #  combine year_wave
    mutate(year_wave = paste(year, wave, sep = "_")) %>%
  # split by sa_gom column into 2
    split(as.factor(fhier_mrip_catch_by_species_state_region_waves$sa_gom))

# View(fhier_mrip_catch_by_species_state_region_waves_sa_gom_list_tmp)

# remove extra columns in each df
fhier_mrip_catch_by_species_state_region_waves_sa_gom_list <-
  map(fhier_mrip_catch_by_species_state_region_waves_sa_gom_list_tmp,
      .f = list(. %>% dplyr::select(-one_of("year", "wave", "sa_gom")
                                    )
                )
  )

# glimpse(fhier_mrip_catch_by_species_state_region_waves_sa_gom_list)

```

## get 10 most frequent spp. by region
```{r get 10 most frequent spp. by region}

n_most_frequent_fhier_10_list <- 
  fhier_mrip_catch_by_species_state_region_waves_sa_gom_list %>%
  # for each region
  map(function(x) {x %>%
      select(species_itis, fhier_catch_by_4) %>%
      group_by(species_itis) %>%
      summarise(fhier_catch_by_spp = sum(fhier_catch_by_4)) %>%
      arrange(desc(fhier_catch_by_spp)) %>%
      head(10)
    
})
n_most_frequent_fhier_10_list$gom %>% head()

```


## why numbers for fhier bass are low?
```{r why numbers for fhier bass are low?}
a1 <-
fhier_mrip_catch_by_species_state_region_waves_sa_gom_list$gom %>%
  filter(species_itis %in% n_most_frequent_fhier_10_list$gom$species_itis)

fhier_mrip_catch_by_species_state_region_waves_sa_gom_top_10f <-
  full_join(fhier_mrip_catch_by_species_state_region_waves_sa_gom_list$gom,
  n_most_frequent_fhier_10_list$gom)
# Joining with `by = join_by(species_itis)`

View(fhier_mrip_catch_by_species_state_region_waves_sa_gom_top_10f)
glimpse(fhier_mrip_catch_by_species_state_region_waves_sa_gom_top_10f)
fhier_mrip_catch_by_species_state_region_waves_sa_gom_top_10f %>%
  filter(common_name.x == "BASS, BLACK SEA") %>%
  group_by(sa_gom) %>% str()
  summarise(catch_sum = sum(fhier_quantity_by_4))

fhier_quantity_by_species_permit_state_region_waves %>%
  filter(common_name == "BASS, BLACK SEA" & end_year == "2022") %>%
  group_by(end_port_sa_gom) %>%
  summarise(catch_sum = sum(fhier_quantity_by_4 ))
```

