---
title: "Geo errors"
date: today
output:
  html_document
format:
  html:
    toc: true
    # toc-depth: 2
    css: styles.css
    code-overflow: wrap
    # code-fold: true
    code-summary: "Show the code"
    code-line-numbers: true
---

## Setup
```{r setup}
# setup ----
library(mapview)
library(ggplot2)
library(ggmap)

library(rnaturalearth)
library(rnaturalearthdata)

source("~/R_code_github/useful_functions_module.r")
my_paths <- set_work_dir()
current_project_dir_path <-
  file.path(my_paths$git_r, "fishing_effort_location")

```

# Get data
```{r get data}
# get data ----
# "C:\Users\anna.shipunova\Documents\R_code_github\get_db_data\get_db_data.R"
source(file.path(my_paths$git_r, r"(get_db_data\get_db_data.R)"))

tic("run_all_get_db_data()")
all_get_db_data_result_l <- run_all_get_db_data()
toc()
# run_all_get_db_data(): 2.27 sec elapsed (from csv)

trip_coord_info <-
  all_get_db_data_result_l[["trip_coord_info"]] |>
  remove_empty_cols()

world_coast <-
  rnaturalearth::ne_coastline(returnclass = "sf")
# class(world_coast)

```

## Statistics
```{r statistics}

# statistics ----

dim(trip_coord_info)
# [1] 141350     39

# data_overview(trip_coord_info)

coordInfo_summ <- summary(trip_coord_info) |>
  as.data.frame()

coordInfo_summ_compact <-
  coordInfo_summ |>
  select(-Var1) |>
  tidyr::pivot_wider(names_from = Var2,
              # number of vessels
              values_from = Freq,
              values_fn = list)

# coordInfo_summ_compact$FISHING_HOURS

# str_split_fixed(coordInfo_summ$Freq, " *: *", 2) |> head()

coordInfo_summ1 <-
  coordInfo_summ |>
  tidyr::separate(Freq, c("stat_name", "sta_val"), " *: *",
                  extra = "merge")

# View(coordInfo_summ1)

coordInfo_summ2 <-
  coordInfo_summ1 |>
  distinct() |>
  pivot_wider(names_from = stat_name,
              id_cols = Var2,
              values_from = sta_val) |>
  # mutate_if(is.character, trimws) |>
  mutate(field_name = trimws(Var2),
         .before = 1,
         .keep = "unused")

names(coordInfo_summ2) <- fix_names(names(coordInfo_summ2))

# print_df_names(coordInfo_summ2)

coordInfo_summ2_short <-
  coordInfo_summ2 |>
  filter(is.na(mode)) |>
  select(field_name, min, max, na_s) |>
  distinct()

# View(coordInfo_summ2_short)

# coordInfo_summ2_short$field_name |> cat(sep = ", ")
# TRIP_ID, FISHING_HOURS, LATITUDE, LONGITUDE, AVG_DEPTH_IN_FATHOMS, E_DE, E_DC, DEPTH, MINIMUM_BOTTOM_DEPTH, MAXIMUM_BOTTOM_DEPTH, FISHING_GEAR_DEPTH, DAYS_AT_SEA, T_DE, T_DC, VESSEL_ID, CF_PERMIT_ID, TRIP_START_DATE, TRIP_END_DATE, ACTIVITY_TYPE, SERO_VESSEL_PERMIT

weird_stats <-
  coordInfo_summ2_short |>
  filter(field_name %in%
           c("FISHING_HOURS", "LATITUDE", "LONGITUDE", "TRIP_END_DATE"))

head(weird_stats)
#   field_name    min                        max                        na_s
# 1 FISHING_HOURS "0.000  "                  "4920.640  "                NA
# 2 LATITUDE      "-87.30  "                 "90.00  "                  "580  "
# 3 LONGITUDE     "-117.25  "                "137.59  "                 "580  "
# 4 TRIP_END_DATE "1969-08-17 00:00:00.00  " "2023-09-19 00:00:00.00  "  NA

```

# errors in geo data ----
# 1) a sign
# 2) on land
# 3) outside boundaries
# 3a) if 28 north - see the wrong long?
# 4) wrong depth
# 5) missing coords
# filter(complete.cases(.)) %>%
# 6) area codes?
# AREA_CODE               91
# SUB_AREA_CODE           56
# DISTANCE_CODE_NAME       5
# LOCAL_AREA_CODE         46

# ===
# fathom, old English measure of length, now standardized at 6 feet (1.83 metre), which has long been used as a nautical unit of depth.

# ===
# LATITUDE      NA's   :1198
# LATITUDE        LONGITUDE
# Min.   :-87.30   Min.   :-117.25
# Max.   : 90.00   Max.   : 137.59

## Map functions
```{r map functions}
# sa_shp <-
#   sf::read_sf(r"(~\R_files_local\my_inputs\shapefiles\osa_n_gom\SA_EEZ_off_states.shp)")
# 
# gom_shp <- 
#   sf::read_sf(r"(~\R_files_local\my_inputs\shapefiles\osa_n_gom\ReefFish_EFH_GOM.shp)")

# federal_state_waters_shp <-
# sf::read_sf(r"(~\R_files_local\my_inputs\shapefiles\federal_and_state_waters\FederalAndStateWaters.shp)")
# dim(federal_state_waters_shp)
# [1] 40  7

federal_state_waters_east_shp <-
sf::read_sf(r"(~\R_files_local\my_inputs\shapefiles\FederalandStat_east\FederalandStat_east.shp)")
dim(federal_state_waters_east_shp)
# 1 7

# "C:\Users\anna.shipunova\Documents\R_files_local\my_inputs\shapefiles\USMaritimeLimi_ExportFeature_east\USMaritimeLimi_ExportFeature_east.shp"

USMaritimeLimi_ExportFeature_shp <-
sf::read_sf(r"(~\R_files_local\my_inputs\shapefiles\USMaritimeLimitsAndBoundariesSHP_orig\USMaritimeLimitsNBoundaries.shp)")

str(USMaritimeLimi_ExportFeature_shp)
# [1] 260  17

# class(USMaritimeLimi_ExportFeature_shp)
USMaritimeLimi_ExportFeature_east_shp <-
  USMaritimeLimi_ExportFeature_shp |> 
  filter(REGION == "Atlantic Coast and Gulf of Mexico")

# mapview(USMaritimeLimi_ExportFeature_east_shp)
# [1] 49 17

# bbox <-
#   st_bbox(big_bounding_box, 
#           crs = st_crs(federal_state_waters_shp)) |> 
#   st_as_sfc()

# mapview(bbox)

# federal_state_waters_shp_east <-
#     sf::st_crop(federal_state_waters_shp,
#               big_bounding_box)
# 
# str(federal_state_waters_shp)
# [1] 0 7

# mapview(federal_state_waters_shp_east)


# "C:\Users\anna.shipunova\Documents\R_files_local\my_inputs\shapefiles\USMaritimeLimitsAndBoundariesSHP\USMaritimeLimitsNBoundaries.shp"
# USMaritimeLimitsNBoundaries_shp <-
# sf::read_sf(r"(~\R_files_local\my_inputs\shapefiles\USMaritimeLimitsAndBoundariesSHP\USMaritimeLimitsNBoundaries.shp)")
# dim(USMaritimeLimitsNBoundaries_shp)

# mapview(USMaritimeLimitsNBoundaries_shp)
# [1] 62 17

my_crs <- sf::st_crs(USMaritimeLimitsNBoundaries_shp)

lat_long_to_map <- 
  function(my_df, my_title = "my_title", legend = TRUE) {
  my_df %>%
    # save info to show on the map
    dplyr::mutate(point = paste(LATITUDE, LONGITUDE, sep = ", ")) %>%
    # convert to sf
    # an sf object is a collection of simple features that includes attributes and geometries in the form of a data frame.
    sf::st_as_sf(coords = c("LONGITUDE",
                        "LATITUDE"),
                 crs = my_crs) %>%
    mapview::mapview(
      col.regions = viridisLite::turbo,
      layer.name = my_title,
      legend = legend
    ) %>% return()
}

lat_long_to_map_plot <-
  function(my_df,
           my_title = "my_title") {
    my_df_sf <-
      my_df %>%
      # save info to show on the map
      dplyr::mutate(point = paste(LATITUDE, LONGITUDE, sep = ", ")) %>%
      # convert to sf
      # an sf object is a collection of simple features that includes attributes and geometries in the form of a data frame.
      sf::st_as_sf(coords = c("LONGITUDE",
                              "LATITUDE"),
                   crs = my_crs)
    
    map_plot <-
      ggplot() +
      ggplot2::geom_sf(data = world_coast) +
      ggplot2::geom_sf(data = my_df_sf,
                       color = "blue") +
      ggplot2::ggtitle(my_title)
    
      return(map_plot)
    
  }

crop_by_shape <-
  function(my_sf, shape) {
    my_sf |>
      sf::st_join(shape, left = FALSE) %>%
      dplyr::mutate(
        LONGITUDE = sf::st_coordinates(.)[, 1],
        LATITUDE = sf::st_coordinates(.)[, 2]
      ) %>%
      return()
  }


```

## Map all points
```{r map all points}

trip_coord_info_map_data <-
  trip_coord_info |>
  select(LONGITUDE, LATITUDE) |>
  distinct() |>
  dplyr::filter(!is.na(LONGITUDE) | !is.na(LATITUDE)) |>
  mutate(label_lat_lon = paste(round(LATITUDE, 0),
                               round(LONGITUDE, 0)))
  # dim()
  # [1] 116246      3

trip_coord_info_plot <-
  lat_long_to_map_plot(trip_coord_info_map_data,
                       "All coordinates")
trip_coord_info_plot

# trip_coord_info_mapview <-
#   trip_coord_info_map_data |>
#   mapview::mapview(
#     # colors according a chosen column
#     zcol = "label_lat_lon",
#     # palette to choose colors from
#     col.regions = viridisLite::turbo,
#     layer.name = 'label_lat_lon',
#     # transparency
#     alpha = 0.3,
#     legend = FALSE
#   )
```

## Sign
### Positive longitude
```{r Sign}
# 1) a sign ----
## positive_long ----
positive_long <-
  trip_coord_info %>%
  filter(LONGITUDE > 0)

dim(positive_long)

#     LATITUDE        LONGITUDE
# Min.   :-87.30   Min.   :-117.25
# 1st Qu.: 26.10   1st Qu.: -83.57
# Median : 29.00   Median : -81.01
# Mean   : 28.88   Mean   : -50.88
# 3rd Qu.: 30.16   3rd Qu.: -75.85
# Max.   : 90.00   Max.   : 137.59
# NA's   :1277     NA's   :1277

positive_long_map <-
  positive_long |> 
  select(LATITUDE, LONGITUDE) |> 
  lat_long_to_map_plot('Positive longitude')

positive_long_map

```

### Negative latitude
```{r negative latitude}
### negative latitude ----
negative_lat <-
  trip_coord_info %>%
  filter(LATITUDE <= 0)

dim(negative_lat)
# 120

negative_lat %>% select(LATITUDE, LONGITUDE) %>% distinct()
glimpse(negative_lat)
negative_lat %>% count(LATITUDE, LONGITUDE)
# LATITUDE LONGITUDE  n
# 1 -87.30000  29.30000  2
# 2 -83.97695  29.15705 11
# 3 -76.76466  55.33196  3
# 4 -41.40274 -14.40965  2
# 5 -30.00000  86.00000 93
# 6 -27.85917 137.58650  4
# 7   0.00000   0.00000  5
```


### Negative latitude mapped
```{r Wrong sign mapped}
negative_lat_c_subset <-
  negative_lat %>%
  select(LATITUDE, LONGITUDE)

neg_lat_map <-
  lat_long_to_map_plot(negative_lat_c_subset, 'Negative latitude')
  
neg_lat_map

```

## Outside boundaries
```{r outside boundaries}
## 3) outside boundaries ----
big_bounding_box <- c(
   xmin = -97.79954,
   ymin = 21.521757, #Cuba
   xmax = -64.790337, #Bermuda
   ymax = 49 #Canada
 )

trip_coord_info_short_sf <-
  trip_coord_info |>
  select(LATITUDE, LONGITUDE) |>
  distinct() |>
  dplyr::filter(!is.na(LONGITUDE) | !is.na(LATITUDE)) |>
  sf::st_as_sf(
    coords = c("LONGITUDE",
               "LATITUDE"),
    crs = my_crs
  )

str(trip_coord_info_short_sf)
# [1] 116246      1

# trip_coord_info_sf_outside_big_box <-
#     trip_coord_info_sf |>
#       # sf::st_join(GOMsf, left = FALSE) %>%
#       dplyr::mutate(LONGITUDE = sf::st_coordinates(.)[, 1],
#              LATITUDE = sf::st_coordinates(.)[, 2])

trip_coord_info_crop_big_sf <-
  sf::st_crop(trip_coord_info_short_sf,
              big_bounding_box)

dim(trip_coord_info_crop_big_sf)
# [1] 111572      1

trip_coord_info_sf_out <-
  trip_coord_info_short_sf |>
  filter(lengths(
    sf::st_intersects(trip_coord_info_short_sf, trip_coord_info_crop_big_sf)
  ) == 0)

dim(trip_coord_info_crop_big_sf)
# [1] 111572      1

dim(trip_coord_info_sf_out)
# [1] 4674    1

str(trip_coord_info_sf_out)

out_of_boxmap_plot <-
  ggplot() +
  ggplot2::geom_sf(data = world_coast) +
  ggplot2::geom_sf(data = trip_coord_info_sf_out,
                       color = "blue") +
  geom_rect(
    aes(
      xmin = big_bounding_box[["xmin"]],
      xmax = big_bounding_box[["xmax"]],
      ymin = big_bounding_box[["ymin"]],
      ymax = big_bounding_box[["ymax"]]
    ),
    color = "red",
    fill = NA
  ) +
  ggplot2::ggtitle("Points outside of the big box")

out_of_boxmap_plot

# rectangular_big_box_view <- mapview::viewExtent(trip_coord_info_crop_big_sf)
# 
# mapview::mapview(trip_coord_info_sf_out) +
#   rectangular_big_box_view

```

## On land
### Shape files maps
```{r 2) on land}
## 2) on land ----
  # trip_coord_info_crop_big_sf

# corrected_data_map <- corrected_data_sf %>% mapview()
# View(corrected_data_map)
# 11998

```

### Inside SA and GOM
```{r inside sa and gom}
### Inside SA and GOM ----

trip_coord_info_sf_in <-
  trip_coord_info_short_sf |>
  filter(lengths(
    sf::st_intersects(trip_coord_info_short_sf, trip_coord_info_crop_big_sf)
  ) > 0)

dim(trip_coord_info_sf_in)
# [1] 111572      1

trip_coord_info_sf_in_all <-
  trip_coord_info_short_sf |>
  filter(lengths(
    sf::st_intersects(trip_coord_info_short_sf, USMaritimeLimi_ExportFeature_east_shp)
  ) > 0)

sf::st_bbox(USMaritimeLimi_ExportFeature_east_shp)
#      xmin      ymin      xmax      ymax 
# -97.15469  23.81794 -65.69948  45.07451 
# mapview(federal_state_waters_east_shp)
# View(USMaritimeLimi_ExportFeature_east_shp)


# federal_state_waters_east_shp$geometry |> 
#   str()
# sfc_POLYGON of length 1; first list element: List of 36988
# ...
 # - attr(*, "class")= chr [1:3] "XY" "POLYGON" "sfg"

# USMaritimeLimi_ExportFeature_east_shp$geometry[[4]]
# MULTILINESTRING ((-73.47384 40.18069, -73.46701 40.18175, -73.45811 40.18326, -73.44925 40.18488, ...

# View(trip_coord_info_crop_big_sf)
# too slow:
tic("in_sa_gom_inters")
in_sa_gom_inters <-
  sf::st_intersection(trip_coord_info_crop_big_sf, USMaritimeLimitsNBoundaries_shp)
toc()

sf::st_crs(federal_state_waters_east_shp)
  # User input: WGS 84 / World Mercator 
    # ID["EPSG",3395]]

sf::st_crs(trip_coord_info_crop_big_sf)
    # ID["EPSG",4326]]

# ---
trip_coord_info_short_sf1 <-
  trip_coord_info |>
  select(LATITUDE, LONGITUDE) |>
  distinct() |>
  dplyr::filter(!is.na(LONGITUDE) | !is.na(LATITUDE)) |>
  sf::st_as_sf(
    coords = c("LONGITUDE",
               "LATITUDE"),
    crs = sf::st_crs(federal_state_waters_east_shp)
  )

trip_coord_info_crop_big_sf1 <-
  sf::st_crop(trip_coord_info_short_sf1,
              big_bounding_box)

# ----
tic("in_sa_gom_diff")
in_sa_gom_diff <-
  sf::st_difference(trip_coord_info_crop_big_sf1, federal_state_waters_east_shp)
toc()
dim(in_sa_gom_diff)



dim(in_sa_gom_inters)

# str(USMaritimeLimitsNBoundaries_shp)

dim(trip_coord_info_crop_big_sf)
# [1] 111572      1

tic("minus_sa_gom")
minus_sa_gom <-
  # trip_coord_info_crop_big_sf |>
  sf::st_filter(trip_coord_info_crop_big_sf,
                sf::st_union(in_sa_gom),
                .predicate = sf::st_disjoint)
toc()
str(minus_sa_gom)


# mapview(in_sa_gom_inters)
# all.equal(sf::st_crs(trip_coord_info_crop_big_sf),
            # User input: WGS 84 / World Mercator 

# sf::st_crs(USMaritimeLimitsNBoundaries_shp))

# tic("in_sa_gom")
# in_sa_gom <-
#   crop_by_shape(trip_coord_info_crop_big_sf, USMaritimeLimitsNBoundaries_shp)
# toc()
# in_sa_gom: 3.1 sec elapsed

dim(in_sa_gom)
# 
# in_sa <-
#   crop_by_shape(trip_coord_info_crop_big_sf, federal_state_waters_east_shp)
# 
# dim(in_sa)
# # [1] 32846     5
# 
# in_gom <-
#   crop_by_shape(trip_coord_info_crop_big_sf, gom_shp)
# 
# dim(in_gom)
# [1] 37312     5
```

### Not in SA and GOM
```{r not in sa and gom}
### not in sa and gom ----

# stop here 
tic("minus_sa_gom")
minus_sa_gom <-
  # trip_coord_info_crop_big_sf |>
  sf::st_filter(trip_coord_info_crop_big_sf,
                sf::st_union(in_sa_gom),
                .predicate = sf::st_disjoint)
toc()
str(minus_sa_gom)
# 0 1
# minus_sa_gom: 2.09 sec elapsed

mapview(minus_sa_gom) +
  mapview(sa_shp)

tic("minus_gom")
minus_sa_gom <-
  # trip_coord_info_crop_big_sf |>
  st_filter(minus_sa,
            st_union(in_gom), .predicate = st_disjoint)
toc()
# minus_gom: 15.84 sec elapsed
  
mapview(minus_sa_gom) +
  mapview(sa_shp, fill = "lightgreen") +
  mapview(gom_shp, fill = "lightgreen")

 # sf::st_difference(trip_coord_info_crop_big_sf, sa_shp)
# Warning message:
# attribute variables are assumed to be spatially constant throughout all geometries

# sf_use_s2(FALSE)
# Spherical geometry (s2) switched off
# 
# minus_gom <- st_difference(corrected_data_sf, gom_shp)

dim(minus_sa)
# [1] 44023    20

# minus_sa_gom <- st_difference(gom_shp, minus_sa)
minus_sa_gom2 <- st_difference(minus_sa, gom_shp)

mm + m_g + m_s
# m_s is still resent?

# A helper function that erases all of y from x: ----
st_erase = function(x, y) st_difference(x, st_union(st_combine(y)))

names(corrected_data) %>% paste0(collapse = ", ")

corrected_data_short_sf <-
  corrected_data %>%
  select(
    TRIP_START_DATE,
    TRIP_END_DATE,
    LATITUDE,
    LONGITUDE,
    MINIMUM_BOTTOM_DEPTH,
    MAXIMUM_BOTTOM_DEPTH,
    FISHING_GEAR_DEPTH
  ) %>%
  st_as_sf(coords = c("LONGITUDE",
                      "LATITUDE"),
           crs = st_crs(sa_shp))

# str(corrected_data_short_sf)
# Classes ‘sf’ and 'data.frame':	11998 obs. of  6 variables:

# st_difference(corrected_data_short_sf,
#               st_union(st_combine(c(gom_shp, sa_shp))))

union_shp <- st_union(gom_shp, sa_shp)
# although coordinates are longitude/latitude, st_union assumes that they are planar
# Warning message:
# attribute variables are assumed to be spatially constant throughout all geometries

plot(union_shp)

# st_difference(corrected_data_short_sf,
#               st_union(st_combine(c(gom_shp, sa_shp))))

corrected_data_short_minus_union_shp <-
  st_difference(corrected_data_short_sf, union_shp)
# although coordinates are longitude/latitude, st_difference
# assumes that they are planar

# write_csv(corrected_data_short_minus_union_shp, "short_minus_sa_gom.csv")

m_minus <- mapview(corrected_data_short_minus_union_shp, color = "green")
# View(corrected_data_short_minus_union_shp)

m_minus + mapview(union_shp)

# minus sa again? ----

all_minus_sa <-
  st_difference(corrected_data_short_minus_union_shp, sa_shp)

write_csv(all_minus_sa, "all_minus_sa.csv")

m_all_minus_sa <-
  mapview(
    all_minus_sa,
    col.regions = "green",
    layer.name = 'Not in GOM or SA',
    alpha = 0.3,
    cex = 1
  )

m_all_minus_sa + union_shp
# ===

# FL ---
# https://catalog.data.gov/dataset/tiger-line-shapefile-2019-state-florida-current-place-state-based/resource/fcf74536-aeab-4ed1-a9df-06daf29a527b

fl_shp <- read_shapefile("tl_2019_12_place_FL/tl_2019_12_place.shp")

st_crs(fl_shp)
    # ID["EPSG",4269]]

on_land <- st_intersection(corrected_data_short_sf, fl_shp)
dim(on_land)
# [1] 3660   22

m_l <- mapview(on_land)
```

